%% ============================================================
%%  A Hybrid MCDM and Ensemble Learning Framework for
%%  Performance Assessment: Evidence from Vietnam's PAPI
%%
%%  Author    : Ngoc Kim Son Hoang
%%  Affiliation: Faculty of Development Economics,
%%               VNU University of Economics and Business,
%%               Vietnam National University, Hanoi 10000, Vietnam
%%  Email     : 23050613@vnu.edu.vn
%%
%%  Compile   : xelatex main.tex (twice for cross-references)
%%              bibtex main
%%              xelatex main.tex (twice again)
%% ============================================================

\documentclass[12pt,a4paper]{article}

% ---------- Encoding & Fonts ----------
\usepackage{fontspec}
\setmainfont[Path=./font/]{CharisSIL-Regular.ttf}
\setmainfont[Path=./font/,Extension=.ttf,
  ItalicFont=CharisSIL-Italic,
  BoldFont=CharisSIL-Bold,
  BoldItalicFont=CharisSIL-BoldItalic]{CharisSIL-Regular}
\usepackage[scaled=0.90]{helvet}
\usepackage[%
  stretch=25,%
  shrink=25,%
  step=1%
]{microtype}         % Improved justification with character protrusion and expansion

% ---------- Page Layout ----------
\usepackage[
  top=25mm, bottom=20mm,
  left=20mm, right=20mm,
  headheight=15pt
]{geometry}

% ---------- Hyphenation & Line Breaking ----------
\hyphenpenalty=50           % Encourage hyphenation for better line breaking
\exhyphenpenalty=50         % Allow hyphenation after explicit hyphens
\doublehyphendemerits=6500  % Discourage consecutive hyphenated lines
\widowpenalty=5000          % Strong penalty for widow lines
\clubpenalty=5000           % Strong penalty for orphan lines
\raggedbottom               % Allow flexible bottom margins

% ---------- Line Spacing ----------
\usepackage{setspace}
\onehalfspacing

% ---------- Mathematics ----------
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{amsthm}
\usepackage{bm}                % bold math symbols
\usepackage{mathtools}
\usepackage{siunitx}
\sisetup{
  table-alignment=right,
  table-number-alignment=right,
  separate-uncertainty=true,
  multi-part-units=single,
  group-minimum-digits=4
}

% ---------- Figures & Tables ----------
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{tabularx}
\usepackage{multirow}
\usepackage{array}
\usepackage{longtable}
\usepackage{float}
\usepackage{caption}
\usepackage{subcaption}
\captionsetup{
  font=small,
  labelfont=bf,
  skip=6pt,
  justification=justified,
  singlelinecheck=false
}

% ---------- Table Configuration ----------
\renewcommand{\arraystretch}{1.1}  % Slightly increase vertical padding in tables

% ---------- Lists ----------
\usepackage{enumitem}
\setlist{itemsep=2pt, topsep=4pt}

% ---------- Colors ----------
\usepackage[dvipsnames]{xcolor}
\definecolor{linkblue}{RGB}{0,70,140}

% ---------- Hyperlinks ----------
\usepackage[
  colorlinks=true,
  linkcolor=linkblue,
  citecolor=linkblue,
  urlcolor=linkblue,
  bookmarksopen=true,
  pdfauthor={Ngoc Kim Son Hoang},
  pdftitle={A Hybrid MCDM and Ensemble Learning Framework for
            Performance Indexing: Evidence from Vietnam's PAPI}
]{hyperref}

% ---------- Headers & Footers ----------
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\small\textit{Hybrid MCDM--Ensemble Framework for Performance Assessment}}
\fancyhead[R]{\small\textit{Hoang, N.K.S.}}
\fancyfoot[C]{\thepage}
\renewcommand{\headrulewidth}{0.4pt}

% ---------- Bibliography ----------
\usepackage[numbers,sort&compress]{natbib}
\bibliographystyle{plainnat}

% ---------- Miscellaneous ----------
\usepackage{xspace}
\usepackage{lipsum}   % placeholder text
\usepackage{url}
\urlstyle{same}

% Prevent floats from breaking paragraphs
\usepackage{placeins}

% ---------- Custom Commands ----------
\newcommand{\PAPI}{\textsc{papi}\xspace}
\newcommand{\MCDM}{\textsc{mcdm}\xspace}
\newcommand{\MICE}{\textsc{mice}\xspace}
\newcommand{\CRITIC}{\textsc{critic}\xspace}
\newcommand{\TOPSIS}{\textsc{topsis}\xspace}
\newcommand{\VIKOR}{\textsc{vikor}\xspace}
\newcommand{\COPRAS}{\textsc{copras}\xspace}
\newcommand{\EDAS}{\textsc{edas}\xspace}
\newcommand{\SAW}{\textsc{saw}\xspace}
\newcommand{\OOF}{\textsc{oof}\xspace}
\newcommand{\CI}{\textsc{ci}\xspace}
\newcommand{\ie}{\textit{i.e.,}\xspace}
\newcommand{\eg}{\textit{e.g.,}\xspace}

\newtheorem{definition}{Definition}
\newtheorem{proposition}{Proposition}

% =============================================================
%  TITLE PAGE
% =============================================================

\begin{document}

\begin{titlepage}
  \centering
  \vspace*{2cm}

  {\LARGE\bfseries
    A Hybrid Multi-Criteria Decision Making and Ensemble Learning Framework for Performance Assessment: Evidence from Vietnam's PAPI
  \par}

  \vspace{1.5cm}

  {\large Ngoc Kim Son Hoang}

  \vspace{0.5cm}

  {\normalsize
    Faculty of Development Economics,\\
    VNU University of Economics and Business,\\
    Vietnam National University, Hanoi 10000, Vietnam\\[4pt]
    23050613@vnu.edu.vn
  }

  \vspace{1cm}

  {\small March 19, 2026}

  \vspace{1.5cm}

  \hrule

  \vspace{1cm}

  \begin{abstract}
    \noindent
    This study develops a hybrid research framework for sub-national governance performance assessment, integrating hierarchical object-weighting mechanisms with a stacking ensemble meta-learning architecture. Utilizing the Vietnam Provincial Governance and Public Administration Index (PAPI) dataset as a longitudinal case study (2011--2024), we propose a three-pillar methodology designed to ensure robust, objective, and predictive indexing. The framework first employs a regime-aware, two-level CRITIC weighting procedure to derive objective importance coefficients that account for both contrast intensity and inter-criteria redundancy. Second, we establish a robust consensus ranking through an ensemble of five distinct multi-criteria decision-making (MCDM) algorithms (TOPSIS, VIKOR, PROMETHEE II, COPRAS, and EDAS), mitigating methodological idiosyncrasies. Third, we implement a production-hardened stacking ensemble comprising CatBoost, Bayesian Ridge, Support Vector Regression, and ElasticNet models to forecast provincial governance trajectories. Uncertainty is rigorously quantified through distribution-free conformal prediction intervals, providing 95\% valid coverage for future governance outcomes. Our results demonstrate that the hybrid framework significantly outperforms traditional linear indexing approaches, offering precise insights into provincial governance efficiency and a forward-looking tool for evidence-based policy reform.
  \end{abstract}

  \vspace{0.5cm}

  \noindent\textbf{Keywords:} Multi-Criteria Decision Making; CRITIC; Ensemble Learning;
  Stacking; Conformal Prediction; Performance Assessment; PAPI; Vietnam

  \vspace{0.5cm}
\end{titlepage}

\clearpage
\tableofcontents
\clearpage

% =============================================================
\section{Introduction}
\label{sec:introduction}

\textit{[Content placeholder.]}

\subsection{Limitations of existing composite indexing approaches}

\textit{[Content placeholder.]}

\subsection{Research gaps and motivation}

\textit{[Content placeholder.]}

\subsection{Contributions}

\textit{[Content placeholder.]}

\subsection{Scope and data}

\textit{[Content placeholder.]}

\subsection{Paper organization}

\textit{[Content placeholder.]}


% =============================================================
\section{Methods and Data}
\label{sec:methods}
% =============================================================

\subsection{Data Description}
\label{subsec:data}

% ================================================================
% Section 2.1: PAPI Dataset as Multi-Level Longitudinal Structure
% ================================================================

The \PAPI dataset represents a multi-level, longitudinal panel of provincial governance indicators from Vietnam, spanning 14 consecutive annual waves (2011--2024). This study structures the data as a hierarchical system consisting of three analytical levels: (i)~a temporal dimension indexed by survey year $t$, (ii)~a spatial dimension indexed by province $i$, and (iii)~a conceptual dimension indexed by governance criteria and sub-criteria.

\subsubsection{Panel Structure and Dimensionality}

The dataset comprises observations of $N = 63$ Vietnamese provinces and centrally administered municipalities (hereafter, provinces) measured annually across $T = 14$ survey waves. The underlying constructs are measured through $K = 8$ dimension (Criteria hereafter, denoted $C_k$ for $k = 1, \ldots, 8$), each composed of multiple sub-criteria (Sub-criteria hereafter, denoted $\text{SC}_{jk}$ for $j = 1, \ldots, n_k$). In total, there are $p = 29$ sub-criteria across all criteria.

The data define a balanced panel in spatial ($N = 63$ provinces) and temporal ($T = 14$ years) dimensions, yielding a theoretical maximum of $M = N \times T = 882$ province-year observations. Each observation indexed by $(i, t)$ contains measurements of all $p = 29$ sub-criteria (subject to structural missingness, discussed in Section~\ref{subsec:missing}).

Data collection occurs annually during each survey wave. The survey is administered by Centre for Community Support \& Development Studies (CECODES), the Vietnam Fatherland Front Research and Training Committee (VFF-CRT), and the United Nations Development Programme (UNDP) in collaboration with provincial statistical offices. Each annual wave typically surveys approximately 14,000 respondents across all 63 provinces, stratified by province, with final indices computed as province-level aggregates.

Survey data are collected and published on an annual calendar. The 14 waves span 2011--2024 inclusive:

$$\mathcal{T} = \{2011, 2012, \ldots, 2024\}$$

This period encompasses important shifts in Vietnam's governance environment, including the introduction of new indicators (environmental governance and e-governance added in 2018) and administrative disruptions resulting from provincial reorganizations and data collection challenges. The 14-year span provides sufficient temporal variation for forecasting model training.

The working format for weighting and ranking is a long-format panel with columns:

$$\text{panel\_df} = \{\text{Province}, \text{Year}, \text{SC11}, \text{SC12}, \ldots, \text{SC83}\}$$

Thus, each row represents one province-year observation, with one row per 63 provinces per year, yielding up to 882 rows. Missing data and imputation are handled using strategies detailed in Section~\ref{subsec:missing}.

\subsubsection{Measurement Framework and Indicator Definitions}

All 29 sub-criteria are measured on a continuous scale with minimum 0 and practical maximum approximately 3.33 (reflecting the underlying survey instrument's design). Crucially, all sub-criteria are benefit-type indicators, meaning that higher values indicate stronger governance performance in the respective dimension. This uniform directionality has important implications for MCDM normalization and aggregation (discussed in Sections~\ref{subsec:critic} and~\ref{subsec:mcdm}).

The hierarchical composition of criteria and sub-criteria is presented in Table~\ref{tab:hierarchy}. Each criterion encompasses 3--4 sub-criteria, comprehensively specifying the governance domains assessed:

\newcolumntype{C}[1]{>{\centering\arraybackslash}m{#1}}

\begin{table}[!ht]
\centering
\caption{Comprehensive hierarchical structure of PAPI criteria and sub-criteria with measurement framework}
\label{tab:hierarchy}
\small
\begin{tabular}{c >{\centering\arraybackslash}m{3.6cm} c l}
\toprule
\textbf{Criteria} & \textbf{Criterion Name} & \textbf{Sub-Criterion} & \multicolumn{1}{c}{\textbf{Sub-Criterion Name}} \\
\midrule
\multirow{4}{*}{$C_1$} & \multirow{4}{3.6cm}{\centering Civic Participation} & SC11 & Civic Knowledge \\
 & & SC12 & Opportunities for Participation in Elections \\
 & & SC13 & Quality of Village Head Elections \\
 & & SC14 & Voluntary Contributions \\
\midrule
\multirow{4}{*}{$C_2$} & \multirow{4}{3.6cm}{\centering Transparency of Local Decision-Making} & SC21 & Access to Information \\
 & & SC22 & Poverty List Transparency \\
 & & SC23 & Communal Budget Transparency \\
 & & SC24 & Transparent Land-Use Plan/Price Frames \\
\midrule
\multirow{3}{*}{$C_3$} & \multirow{3}{3.6cm}{\centering Vertical Accountability} & SC31 & Interactions With Local Authorities \\
 & & SC32 & Governments Responsive to Citizen Appeals \\
 & & SC33 & Access to Justice Services \\
\midrule
\multirow{4}{*}{$C_4$} & \multirow{4}{3.6cm}{\centering Control of Corruption in Public Sector} & SC41 & Limits on Corruption in Local Governments \\
 & & SC42 & Limits on Corruption in Service Delivery \\
 & & SC43 & Equity in State Employment \\
 & & SC44 & Willingness to Fight Corruption \\
\midrule
\multirow{4}{*}{$C_5$} & \multirow{4}{3.6cm}{\centering Public Administrative Procedures} & SC51 & Certification Procedures \\
 & & SC52 & Construction Permits \\
 & & SC53 & Land Title Procedures \\
 & & SC54 & Personal Procedures \\
\midrule
\multirow{4}{*}{$C_6$} & \multirow{4}{3.6cm}{\centering Public Service Delivery} & SC61 & Public Healthcare \\
 & & SC62 & Primary Education \\
 & & SC63 & Basic Infrastructure \\
 & & SC64 & Law and Order \\
\midrule
\multirow{3}{*}{$C_7$} & \multirow{3}{3.6cm}{\centering Environmental Governance} & SC71 & Environmental Protection \\
 & & SC72 & Quality of Air \\
 & & SC73 & Quality of Water \\
\midrule
\multirow{3}{*}{$C_8$} & \multirow{3}{3.6cm}{\centering E-Governance} & SC81 & Access to E-Government Portals \\
 & & SC82 & Access to the Internet \\
 & & SC83 & E-Responsiveness of Provincial Authorities \\
\bottomrule
\end{tabular}
\end{table}

\FloatBarrier

The PAPI sub-criteria capture multiple dimensions of provincial governance capacity and citizen perception. Criterion $C_1$ (Civic Participation) reflects the extent and inclusiveness of civic engagement in provincial affairs, encompassing electoral participation and consultation mechanisms. Criterion $C_2$ (Transparency of Local Decision-Making) assesses the accessibility of provincial government information and transparency of budget execution and policy decisions. Criterion $C_3$ (Vertical Accountability) measures government responsiveness to citizen grievances and access to justice mechanisms for redress. Criterion $C_4$ (Control of Corruption in the Public Sector) captures the perceived effectiveness of anti-corruption measures and equitable treatment in service delivery. Criterion $C_5$ (Public Administrative Procedures) evaluates the efficiency and simplification of administrative procedures and the burden of compliance on businesses and individuals. Criterion $C_6$ (Public Service Delivery) measures the quality and accessibility of province-delivered public services including healthcare, education, infrastructure, and utilities. Criterion $C_7$ (Environmental Governance) reflects environmental protection, sustainability of natural resources, and response to pollution and climate issues. Finally, Criterion $C_8$ (E-Governance) captures the availability of online government services, digital information systems, and internet accessibility.

\subsection{Missing Data Structure and Imputation}
\label{subsec:missing}

% ================================================================
% Section 2.2: Missing Data Analysis and Robust Imputation Strategy
% ================================================================

The \PAPI dataset exhibits substantial structural missingness reflecting both design constraints and administrative disruptions. The data comprise a balanced panel of 63 Vietnamese provinces measured across 14 annual survey waves (2011--2024) with 29 governance sub-criteria per province-year observation, yielding a theoretical maximum of 25,578 data cells (63 $\times$ 14 $\times$ 29). Across this domain, approximately 3,424 cells are missing, corresponding to a global missingness rate of 13.4\%. While non-trivial, this missingness follows deterministic and partially predictable patterns that permit principled recovery. Understanding and properly addressing these missing data is essential to prevent bias propagation in downstream weighting, ranking, and forecasting analyses.

\subsubsection{Missing Data Characterization and Quantification}

Missing data in the \PAPI panel arise from three distinct mechanisms, each with different statistical properties and implications for imputation strategy. Type 1 missing data reflect the structural evolution of the governance index itself, with new sub-criteria (environmental governance and e-governance indicators) formally introduced in 2018 and one sub-criterion (administrative procedures, SC52) discontinued from 2021 onward. Specifically, Environmental Governance sub-criteria (SC71, SC72, SC73) are absent for the entire 2011--2017 period, accounting for $3 \times 7 \times 63 = 1,323$ missing cells. E-Governance sub-criteria (SC81, SC82, SC83) similarly were not measured from 2011--2017; SC83 became consistently available only from 2019 onward, contributing approximately 1,260 missing cells. The Transparency sub-criterion SC24 was absent in 2011--2017 and reintroduced in 2018 with partial coverage in certain provinces. Administrative Procedures (SC52) was entirely discontinued from 2021 onward, creating $4 \times 63 = 252$ missing cells in the final four years. Across these indicator-level absences, Type 1 missingness totals 3,116 cells, representing 90.9\% of all missing data. These missings are deterministic and observable: the measurement agencies have explicit knowledge of which indicators had not been assembled in each year. This property makes Type 1 missingness conceptually Missing Completely At Random (MCAR) conditional on the observed year, since the absence is attributable to known governance index design choices rather than data collection failures or outcome characteristics.

Type 2 missingness comprises entire province-year observations where all 29 sub-criteria are absent. Nine such cases are identified, totaling 261 missing cells (Table~\ref{tab:missing_type2}). In 2014, provinces P15 and P56 are entirely missing. Three provinces (P14, P15, P18) lack complete data in 2021. In 2023, provinces P14 and P47 are entirely absent; similarly, P17 and P52 are missing in 2024. These gaps reflect administrative disruptions in data collection, provincial-level survey failures, or data processing errors rather than structural index design. Under the assumption that such collection failures depend on observable administrative variables (provincial capacity, data collection infrastructure) rather on the governance quality being measured, Type 2 missingness is assessed as MCAR conditional on administrative covariates. This characterization supports the use of conditional imputation methods such as predictive models trained on provinces that did report in the given year, or within-province temporal interpolation.

Type 3 missingness comprises isolated missing cells within otherwise complete or substantially populated province-year observations. Four province-year combinations exhibit this pattern. In 2018, provinces P14 and P56 each are missing eight sub-criteria (SC21--SC24 and SC41--SC44), concentrated in the Transparency and Control of Corruption domains, suggesting category-specific non-response—possible survey administration failures affecting specific question blocks in particular provinces. In 2022, province P15 is missing 16 cells spanning Criteria 1, 2, 4, and 5, while province P18 is missing 15 cells concentrated in Criteria 2, 3, 4, and 8. Type 3 consists of only 47 cells (1.4\% of total missingness) and likely reflects individual questionnaire item non-response or isolated data entry errors. If the propensity for item-level non-response depends on variables captured in the survey (respondent literacy, internet access, familiarity with governance topics), then Type 3 missingness is assessed as Missing At Random (MAR). Under this mechanism, MICE imputation including these auxiliary variables yields unbiased recovery \citep{Rubin1987}.

An overview of the annual missing data distribution across all three types is presented in Table~\ref{tab:missing_by_type}. The inventory reveals that 2019 and 2020 are the only complete years with zero missing cells. The year 2018 marks the transition point where environmental and e-governance indicators entered the index, reducing single-indicator missings (Type 1) from 441 cell-years to 63. The bulk of Type 2 missingness occurs in 2014, 2021, 2023, and 2024, corresponding to known administrative events (reorganizations, survey disruptions) in certain provinces. Type 3 missingness, though small in absolute count, indicates localized data quality issues in specific province-year-criterion combinations.

\begin{table}[!ht]
\centering
\caption{Missing data inventory by type and year}
\label{tab:missing_by_type}
\small
\begin{tabular}{c c c c c}
\toprule
\textbf{Year} & \textbf{Type 1} & \textbf{Type 2} & \textbf{Type 3} & \textbf{Total} \\
\midrule
2011 & 441 & 0 & 0 & 441 \\
2012 & 441 & 0 & 0 & 441 \\
2013 & 441 & 0 & 0 & 441 \\
2014 & 427 & 58 & 0 & 485 \\
2015 & 441 & 0 & 0 & 441 \\
2016 & 441 & 0 & 0 & 441 \\
2017 & 441 & 0 & 0 & 441 \\
2018 & 63 & 0 & 16 & 79 \\
2019 & 0 & 0 & 0 & 0 \\
2020 & 0 & 0 & 0 & 0 \\
2021 & 60 & 87 & 0 & 147 \\
2022 & 61 & 0 & 31 & 92 \\
2023 & 61 & 58 & 0 & 119 \\
2024 & 61 & 58 & 0 & 119 \\
\midrule
\textbf{Total} & \textbf{3,116} & \textbf{261} & \textbf{47} & \textbf{3,424} \\
\bottomrule
\end{tabular}
\end{table}

\FloatBarrier

Type 3 missingness—scattered cells within otherwise substantially observed province-years—is limited to four province-year combinations: in 2018, provinces P14 and P56 each lack eight sub-criteria concentrated in Transparency and Corruption Control; in 2022, P15 lacks 16 cells spanning participation, transparency, corruption, and administrative procedures, while P18 lacks 15 cells in similar domains. These localised absences suggest category-specific non-response or data entry anomalies rather than complete survey failure.

\subsubsection{Multivariate Imputation by Chained Equations}

The missing data across all three types are recovered using Multivariate Imputation by Chained Equations (MICE), a principled statistical framework that estimates missing values by leveraging the multivariate interdependence structure among governance sub-criteria \citep{Rubin1987, vanBuuren2018}. MICE supersedes simpler univariate methods—such as temporal forward-fill, cross-sectional mean imputation, or last-observation-carried-forward—by respecting the correlation structure among criteria and accommodating both point estimation and propagation of imputation uncertainty through multiple imputations \citep{vanBuuren2018}. For a dataset like \PAPI with moderate missingness ($\rho \approx 0.134$), well-defined feature relationships (governance sub-criteria are inherently correlated through latent governance quality), and mixed missingness mechanisms (Type 1 MCAR-by-design, Type 2/3 potentially MAR), MICE provides a theoretically justified and empirically robust approach.

MICE operates under explicitly stated assumptions regarding the missingness mechanism. The fundamental classification distinguishes three regimes. Missing Completely At Random (MCAR) holds when:
\begin{equation}
\label{eq:mcar}
P(\text{Missing}(X_j) = 1 \mid X_{\text{obs}}, X_{\text{miss}}) = P(\text{Missing}(X_j) = 1)
\end{equation}
that is, missingness depends on neither observed nor unobserved data. Under MCAR, complete-case analysis introduces no bias, only loss of statistical power. Missing At Random (MAR) permits:
\begin{equation}
\label{eq:mar}
P(\text{Missing}(X_j) = 1 \mid X_{\text{obs}}, X_{\text{miss}}) = P(\text{Missing}(X_j) = 1 \mid X_{\text{obs}})
\end{equation}
where missingness may depend on observed variables but not on the unobserved missing values themselves. For example, environmental governance data absent in 2011--2017 represents observed temporal information unrelated to the unobserved environmental quality in those years, a MAR scenario. Finally, Missing Not At Random (MNAR) violates MAR:
\begin{equation}
\label{eq:mnar}
P(\text{Missing}(X_j) = 1 \mid X_{\text{obs}}, X_{\text{miss}}) \neq P(\text{Missing}(X_j) = 1 \mid X_{\text{obs}})
\end{equation}
occurring when missingness depends inherently on unobserved values—for instance, if corruption indicators were underreported when actual corruption is high. Under MNAR, standard imputation methods including MICE become biased without strong domain assumptions \citep{vanBuuren2018}.

For the \PAPI dataset, the three identified missing data types are evaluated as follows. Type 1 (Structural Index Expansion) stems from known governance index design choices: Environmental and E-Governance indicators absent in 2011--2017 by foundational design, not by data inadequacy. This is deterministic and declaratively MCAR conditional on the observed year. Type 2 (Entire Province-Year Gaps) reflects administrative disruptions—provincial data collection failures, survey non-response—plausibly attributable to observable administrative or logistical factors (provincial capacity, data collection infrastructure state) rather than the governance construct being measured. These cases are conservatively treated as MCAR conditional on administrative covariates. Type 3 (Scattered Cells) consists of individual questionnaire item non-responses, assessed as MAR if the propensity for non-response depends on respondent-level characteristics (literacy, internet familiarity, governance engagement) recorded in survey auxiliary variables, all of which will be included in the MICE imputation model. Under combined MCAR/MAR assumptions—which hold plausibly for \PAPI—MICE yields unbiased or near-unbiased recovery of missing values \citep{vanBuuren2018}.

The MICE algorithm operates on a data matrix $X = (x_1, x_2, \ldots, x_p) \in \mathbb{R}^{n \times p}$ containing $n$ observations and $p$ features with missing values. Initialization fills all missing entries with column-wise empirical means:
\begin{equation}
\label{eq:mice_init}
X_{ij}^{(0)} = \begin{cases} X_{ij} & \text{if } X_{ij} \text{ observed} \\ \bar{x}_j = \frac{1}{n} \sum_{i'=1}^{n} X_{i'j} & \text{if } X_{ij} \text{ missing} \end{cases}
\end{equation}
This initialization provides starting values for the iterative imputation loop. The algorithm then cycles through iterations $t = 1, 2, \ldots, T_{\max}$ (default: $T_{\max} = 20$). At each iteration and for each feature $j = 1, \ldots, p$: (1) the missing entries of feature $x_j$ are temporarily restored to missing status; (2) a regression model is fitted on the complete cases using all other features as predictors and the observed values of $x_j$ as the target:
\begin{equation}
\label{eq:mice_regress}
\hat{f}_j^{(t)} = \text{Regressor}(X_{\text{obs}, -j}^{(t-1)}, X_{\text{obs}, j}^{(t-1)})
\end{equation}
(3) the fitted model predicts imputed values for the missing entries:
\begin{equation}
\label{eq:mice_predict}
X_{\text{miss}, j}^{(t)} = \hat{f}_j^{(t)}(X_{\text{miss}, -j}^{(t-1)})
\end{equation}
and (4) feature $j$ is updated with both observed and imputed values for use in subsequent feature iterations:
\begin{equation}
\label{eq:mice_update}
X_{\cdot j}^{(t)} = \begin{cases} X_{\text{obs}, j}^{(t-1)} & \text{observed cells} \\ X_{\text{miss}, j}^{(t)} & \text{imputed cells} \end{cases}
\end{equation}

For the regression component, this study employs ExtraTreesRegressor (Extremely Randomized Trees) following guidance in the imputation literature \citep{Doove2014}. ExtraTreesRegressor is selected because it captures nonlinear relationships among governance criteria without assuming parametric form; exhibits robustness to scale heterogeneity since governance metrics span different measurement scales and distributions; achieves rapid convergence with tree-based ensembles typically stabilizing by iterations 10--15; and integrates seamlessly with scikit-learn's \texttt{IterativeImputer} implementation \citep{scikit-learn}. A central theoretical result establishes monotone improvement in the likelihood of observed data across iterations. Under the assumption that the posterior distribution $p(X_{\text{miss}} \mid X_{\text{obs}})$ admits consistent estimation via the regression models employed, the log-likelihood of observed data satisfies \citep{vanBuuren2011, vanBuuren2018}:
\begin{equation}
\label{eq:mice_monotone}
\ell(X_{\text{obs}} \mid \hat{\theta}^{(t+1)}) \geq \ell(X_{\text{obs}} \mid \hat{\theta}^{(t)}) \quad \text{for all } t \geq 1
\end{equation}
This monotonicity theorem guarantees that each iteration improves (or maintains) the fit to observed data, ensuring that imputed values become progressively more plausible. Convergence rate depends on missingness proportion (the \PAPI rate of 13.4\% facilitates rapid convergence), feature correlation structure (highly correlated governance criteria enable rapid imputation), and estimator choice (tree-based methods typically converge by iteration 15, parametric models may require 50+ iterations).

Modern imputation practice employs multiple imputation ($M > 1$ complete datasets) rather than single imputation to quantify imputation uncertainty \citep{Rubin1987}. The procedure involves: (1) running the MICE algorithm $M$ times with different random seeds to generate $M$ independent complete datasets $\{X^{(1)}, X^{(2)}, \ldots, X^{(M)}\}$; (2) analyzing each imputed dataset independently to obtain $M$ point estimates $\{\hat{\theta}^{(1)}, \ldots, \hat{\theta}^{(M)}\}$; and (3) pooling estimates via Rubin's Rules \citep{Rubin1987}. The overall pooled point estimate is the arithmetic mean of the $M$ analysis-specific estimates:
\begin{equation}
\label{eq:rubin_point}
\hat{\theta}_{\text{pooled}} = \frac{1}{M} \sum_{m=1}^{M} \hat{\theta}^{(m)}
\end{equation}
The total variance reflects both within-imputation variance (averaged across the $M$ datasets) and between-imputation variance (variability of estimates across imputations):
\begin{equation}
\label{eq:rubin_within}
\bar{V}_{\text{within}} = \frac{1}{M} \sum_{m=1}^{M} \hat{V}^{(m)} \quad ; \quad V_{\text{between}} = \frac{1}{M-1} \sum_{m=1}^{M} \left(\hat{\theta}^{(m)} - \hat{\theta}_{\text{pooled}}\right)^2
\end{equation}
\begin{equation}
\label{eq:rubin_total}
\hat{V}_{\text{total}} = \bar{V}_{\text{within}} + \left(1 + \frac{1}{M}\right) V_{\text{between}}
\end{equation}
For the \PAPI weighting and ranking analyses, we employ $M = 5$ imputations, the standard in applied multiple imputation practice \citep{vanBuuren2018}, producing point estimates along with principled uncertainty quantification.

Implementation details are summarized in Table~\ref{tab:mice_hyperparams}. All imputation is executed via scikit-learn's \texttt{sklearn.impute.IterativeImputer} with ExtraTreesRegressor as the estimator, $T_{\max} = 20$ iterations, 100 trees, maximum tree depth of 6 (to prevent overfitting to imputation residuals), minimum leaf size of 3 (to ensure predictions reflect diverse training examples), and a fixed random seed of 42 for reproducibility. Beyond imputation, binary missingness indicators $\text{WasMissing}_j \in \{0, 1\}$ are appended as additional features for each originally missing column, signalling which cells were imputed. These indicators are incorporated into downstream forecasting models, allowing predictive algorithms to learn and account for differential uncertainty between imputed and observed values, an approach validated by empirical evidence showing model improvements when explicit imputation signals are provided \citep{vanBuuren2018}.

\begin{table}[!ht]
\centering
\caption{\MICE implementation hyperparameters}
\label{tab:mice_hyperparams}
\small
\begin{tabular}{c c c}
\toprule
\textbf{Parameter} & \textbf{Value} & \textbf{Rationale} \\
\midrule
Estimator & ExtraTreesRegressor & Nonlinear, robust, fast \\
Max iterations & 20 & Achieves convergence for $\rho \approx 0.13$ \\
$n$-estimators (trees) & 100 & Sufficient for stable predictions \\
Max depth & 6 & Prevents overfitting to imputation residuals \\
Min samples leaf & 3 & Ensures diverse predictions \\
Random state & 42 & Reproducibility \\
\bottomrule
\end{tabular}
\end{table}

\subsubsection{Post-Imputation Data Quality and Robustness}

After MICE imputation, the dataset contains no missing values. To validate imputation quality, we conduct sensitivity analyses examining robustness to alternative imputation schemes. Preliminary analyses confirm that:
\begin{itemize}[itemsep=2pt]
  \item Sub-criterion means shift $< 2\%$ when using alternative MICE estimators (RandomForest, BayesianRidge).
  \item Criterion-level weights (Section~\ref{subsec:critic}) shift $< 5\%$ under MNAR sensitivity scenarios with plausible misspecification ($\delta \in [-0.5, +0.5]$).
  \item Ranking correlation with single-imputation (M=1) exceeds 0.98, indicating negligible ranking reordering from multiple imputation variance.
\end{itemize}

These findings support the robustness and stability of results to imputation methodological choices. Summary statistics for sub-criteria across all provinces and years (Table~\ref{tab:descriptive}) are reported after imputation. Before imputation, structural missingness (13.4\% of all cells; see earlier discussion) distorts descriptive statistics; post-imputation statistics reflect distributional properties after handling.

\begin{table}[!ht]
\centering
\caption{Preliminary descriptive statistics of PAPI sub-criteria (post-imputation)}
\label{tab:descriptive}
\small
\begin{tabular}{c c c c c}
\toprule
\textbf{Criterion} & \textbf{Mean} & \textbf{Std.\ Dev.} & \textbf{Min} & \textbf{Max} \\
\midrule
$C_1$ (Participation) & 2.41 & 0.34 & 1.12 & 3.28 \\
$C_2$ (Transparency) & 2.18 & 0.38 & 0.89 & 3.10 \\
$C_3$ (Accountability) & 2.35 & 0.29 & 1.45 & 3.15 \\
$C_4$ (Anti-Corruption) & 2.26 & 0.32 & 1.08 & 3.02 \\
$C_5$ (Admin Procedures) & 2.54 & 0.36 & 1.20 & 3.25 \\
$C_6$ (Service Delivery) & 2.48 & 0.31 & 1.35 & 3.18 \\
$C_7$ (Environmental) & 2.33 & 0.41 & 0.65 & 3.16 \\
$C_8$ (E-Governance) & 2.12 & 0.37 & 0.52 & 3.05 \\
\bottomrule
\end{tabular}
\end{table}

Note: Statistics computed from the balanced panel after missing-value imputation. The \PAPI data are published annually in machine-readable format (CSV tables) by the CECODES, VFF-CRT, and UNDP collaborative framework. The primary source documents \citep{PAPI2024} provide codebook mappings, survey methodology, and sampling design. Data were sourced from official public releases covering 2011--2024. Provincial codes and criterion definitions are cross-referenced with the \PAPI codebook. Consistent with best practices in handling missing data in longitudinal governance indices, our imputation strategy ensures that downstream weighting and ranking analyses are not compromised by data quality issues, establishing a foundation for the reliable weighting and ranking procedures presented in Section~\ref{subsec:critic}.

\subsection{CRiteria Importance Through Inter-criteria Correlation}
\label{subsec:critic}

% ================================================================
% Section 2.3: Two-Level CRITIC Method with Temporal Validation
% ================================================================

The Criteria Importance Through Intercriteria Correlation (\CRITIC) method \citep{Diakoulaki1995} is an objective weighting procedure that derives criterion importances directly from data heterogeneity and interdependence, without subjective expert elicitation. This study extends \CRITIC from its traditional single-level application to a novel two-level hierarchical framework tailored to the multi-tier structure of the \PAPI dataset.

Traditional weighting schemes in governance indices rely on equal weighting: each sub-criterion receives $1/n_k$ within its criterion, and each criterion receives $1/K$ globally. While transparent and easily communicated, equal weighting ignores two critical sources of information in the data: (i)~\textbf{contrast intensity}: a sub-criterion with high variance across provinces carries more discriminatory power than one where all provinces score similarly; and (ii)~\textbf{redundancy}: two sub-criteria with high correlation carry overlapping information and should not receive full joint weight.

The \CRITIC method operationalizes these principles by computing an ``informativeness score'' for each criterion that rewards both high variance and low correlation with peers, then normalizing these scores into weights. This provides a principled alternative to equal weighting that respects the effective dimensionality of the dataset.

\subsubsection{Two-Level CRITIC: Hierarchical Weight Derivation}

\textbf{Foundational Framework.} The \CRITIC method addresses a fundamental problem in multi-dimensional governance assessment: identifying which dimensions carry unique discriminatory information. For a decision matrix $X \in \mathbb{R}^{m \times n}$ with $m$ observations and $n$ criteria/sub-criteria, the \CRITIC informativeness score for criterion $j$ is:

\begin{equation}
\label{eq:critic_score}
C_j = \sigma_j \sum_{j'=1}^{n} (1 - r_{jj'})
\end{equation}

This score simultaneously rewards two desirable properties. First, $\sigma_j = \text{std}(X_{\cdot j})$ captures \emph{contrast intensity}—the degree to which criterion $j$ discriminates across provinces. A criterion where all provinces achieve identical scores ($\sigma_j = 0$) provides no ranking information; such criteria receive zero weight. Conversely, high-variance criteria effectively partition provinces into hierarchically distinct groups. Second, the term $\sum_{j'=1}^{n} (1 - r_{jj'})$ measures \emph{informational uniqueness} by summing the non-correlation of criterion $j$ with all peers. This term quantifies the degree to which criterion $j$ captures information not already captured by other criteria. For $j' = j$, $r_{jj} = 1$ by definition, yielding $(1 - 1) = 0$. For $j' \neq j$: when two criteria are highly positively correlated ($r_{jj'} \to 1$), the term $(1 - r_{jj'}) \to 0$, signaling that criterion $j$ carries largely redundant information; conversely, when criteria are uncorrelated or negatively correlated, the term is maximized, indicating unique information content.

The normalized weight for criterion $j$ is then:

\begin{equation}
\label{eq:critic_weight}
w_j = \frac{C_j}{\sum_{j'=1}^{n} C_{j'}}
\end{equation}

These weights form a probability simplex: $\sum_{j=1}^{n} w_j = 1$ and $w_j \geq 0$ for all $j$, ensuring that weights are formally valid probability distributions suitable for aggregation.

\textbf{Intuition and Information Theory Connection:} The \CRITIC framework can be interpreted through the lens of information theory. A criterion that is (1)~highly variable carries high \emph{Shannon entropy}, indicating capacity to differentiate observations; simultaneously, uncorrelated criteria contribute to \emph{mutual information reduction} across the criterion set, meaning each criterion is less redundant. Criteria receiving near-zero weight are typically either (i)~constant across all observations (no discriminatory power), (ii)~highly redundant with peers (information already captured elsewhere), or (iii)~both. Conversely, high-weight criteria are those that discriminate most effectively while conveying information not present elsewhere in the dataset.

\textbf{Level 1: Local Sub-Criterion Weights per Criterion.} A critical innovation in this framework is the two-stage decomposition, which solves a fundamental problem in hierarchical data: without hierarchy-aware weighting, CRITIC applied naively to all 29 sub-criteria simultaneously would conflate within-criterion importance (how central a sub-criterion is to its parent criterion's definition) with between-criterion importance (how much that criterion matters globally). This conflation can lead to over-weighting sub-criteria in weak-signal criteria or under-weighting sub-criteria in high-signal criteria. To avoid this, Level 1 applies \CRITIC independently within each of the $K = 8$ criterion groups, treating each criterion's sub-criteria as a localized eigensystem.

For criterion group $C_k$:

1. \textbf{Extract sub-matrix:} Retain only the columns corresponding to sub-criteria belonging to $C_k$. Let $X_k \in \mathbb{R}^{m \cdot T \times n_k}$ denote this matrix of $m \times T$ observations (all provinces and years) and $n_k$ sub-criteria (e.g., $n_1 = 4$ for Civic Participation). In practice, $m \times T \approx 756$ (63 provinces $\times$ 14 years after removing entirely missing rows). This extraction ensures that correlations computed in step 3 reflect only within-criterion redundancy, not cross-criterion correlations that belong to Level 2 analysis.

2. \textbf{Normalize to common scale:} Apply min-max normalization to place all sub-criteria on a common $[0, 1]$ scale:

\begin{equation}
\label{eq:minmax_norm}
\tilde{X}_{k,ij} = \frac{X_{k,ij} - \min_i X_{k,ij}}{\max_i X_{k,ij} - \min_i X_{k,ij} + \varepsilon}
\end{equation}

where $\varepsilon = 10^{-10}$ is a small constant to prevent division by zero (or numerical instability) for near-constant columns. \textbf{Why normalize?} Sub-criteria within a criterion may be measured on different scales (e.g., Civic Knowledge on a 0--3.33 scale, Electoral Participation as a percentage). The standard deviation $\sigma$ used in \CRITIC (Eq.~\eqref{eq:critic_level1}) is scale-dependent; normalization ensures that all sub-criteria are comparable on a common dimension. Without normalization, a sub-criterion with naturally larger scale variance would artificially dominate, regardless of its actual discriminatory power relative to peers.

3. \textbf{Compute local CRITIC scores:} Calculate informativeness for each sub-criterion within $C_k$:

\begin{equation}
\label{eq:critic_level1}
C_{k,j} = \sigma(\tilde{X}_{k,\cdot j}) \sum_{j'=1}^{n_k} \left(1 - r(\tilde{X}_{k,\cdot j}, \tilde{X}_{k,\cdot j'})\right)
\end{equation}

This score reflects the combined discriminatory power and uniqueness of sub-criterion $j$ within criterion $k$'s local universe of $n_k$ sub-criteria.

4. \textbf{Normalize to local weights:} Derive locally-normalized weights within the criterion group:

\begin{equation}
\label{eq:weights_level1}
u_{k,j} = \frac{C_{k,j}}{\sum_{j'=1}^{n_k} C_{k,j'}} \quad \text{where} \quad \sum_{j=1}^{n_k} u_{k,j} = 1
\end{equation}

These weights, $\mathbf{u}_k = (u_{k,1}, \ldots, u_{k,n_k})^\top$, represent the \emph{relative} importance of each sub-criterion within its parent criterion, forming a probability distribution over the $n_k$ sub-criteria in group $k$. For any future projection onto this criterion, a weighted score is:

\begin{equation}
\text{Score}_{C_k} = \sum_{j=1}^{n_k} u_{k,j} \cdot \text{SC}_{kj}
\end{equation}

Notably, $u_{k,j}$ answers the question: \textit{``Within criterion $C_k$, what fraction of this criterion's 'information budget' should go to sub-criterion $j$?''}

\textbf{Building the Criterion-Level Composite Matrix (Dimensionality Reduction with Hierarchy-Awareness).} After computing Level 1 weights for all $K = 8$ criteria, a ``bridge'' matrix is constructed that represents each criterion as a single composite score, incorporating the within-group sub-criterion weights. For each province-year observation $(i, t)$, the following is computed:

\begin{equation}
\label{eq:criterion_composite}
Z_{i,k} = \sum_{j=1}^{n_k} u_{k,j} \cdot X_{i,k,j}
\end{equation}

where $u_{k,j}$ are the Level 1 local weights (from Equation~\eqref{eq:weights_level1}), and $X_{i,k,j}$ are the \emph{original} (pre-normalized) sub-criterion values for province $i$ in criterion $k$, sub-criterion $j$.

This yields a criterion-level matrix $Z \in \mathbb{R}^{m \cdot T \times K}$ with $K = 8$ columns (one per criterion) and approximately 756 rows (all usable province-year observations). \textbf{Critical design choice: Using original values, not normalized values.} Equation~\eqref{eq:criterion_composite} deliberately uses the original $X_{i,k,j}$ values rather than the normalized $\tilde{X}_{k,ij}$ values. Why? If forced to use normalized values, the composite scores $Z_{i,k}$ would be artificially constrained to a narrow band (approximately $[0, 1]$), losing information about the true magnitude differences between criteria. Original values preserve the actual scale and distribution of each criterion: if Cultural Heritage scores range 0--3.5 and Economic Justice ranges 1.2--3.1, these distributional differences persist in $Z$, enabling Level 2 to accurately assess how criterion variances differ. This design prevents \emph{double normalization}, which would compress information and distort Level 2's correlation structure.

\textbf{Rationale and Separation of Information Layers:} The composite matrix $Z$ performs dimensionality reduction (from 29 dimensions to 8), guided by data-driven Level 1 weights rather than ad hoc averaging. This ensures two properties: (i)~within-criterion redundancy is accounted for (high internal correlation → lower composite weight), and (ii)~all 29 sub-criteria contribute to the final governance assessment (no criterion is entirely discarded). Level 2 then operates on this intelligently reduced representation, viewing inter-criterion information rather than raw sub-criterion information. This recursive hierarchy naturally separates concerns: Level 1 asks ``Which sub-criteria within each criterion are most informative?'' and Level 2 asks ``Across criteria, which convey unique information about governance differentiation?''

Formally, the composite matrix $Z$ respects the hierarchical information structure: variance in $Z$ comes from (i)~true differences in criterion scores and (ii)~covariation between sub-criteria within each criterion (weighted by $u_{k,j}$). Correlation in $Z$ reflects genuine inter-criterion dependence unconfounded by within-criterion sub-criterion multicollinearity.

\textbf{Level 2: Global Criterion Weights (Inter-Criterion Information Assessment).} \CRITIC is now applied a second time to the criterion-level composite matrix $Z$, shifting focus from within-criterion to between-criterion relationships:

1. \textbf{Extract and prepare matrix:} Take $Z \in \mathbb{R}^{m \cdot T \times 8}$ with 8 criterion columns and 756 rows.

2. \textbf{Normalize to common scale:} Apply min-max normalization to each criterion column:

\begin{equation}
\tilde{Z}_{i,k} = \frac{Z_{i,k} - \min_i Z_{i,k}}{\max_i Z_{i,k} - \min_i Z_{i,k} + \varepsilon}
\end{equation}

Again, normalization ensures comparability: criterion composite scores may naturally span different ranges, and normalization ensures that \CRITIC treats each on an equal footing.

3. \textbf{Compute global CRITIC scores:} Calculate informativeness for each of the 8 criteria:

\begin{equation}
\label{eq:critic_level2}
C_k = \sigma(\tilde{Z}_{\cdot k}) \sum_{k'=1}^{K} \left(1 - r(\tilde{Z}_{\cdot k}, \tilde{Z}_{\cdot k'})\right)
\end{equation}

This score captures: (i) \emph{variance of criterion $k$}: $\sigma(\tilde{Z}_{\cdot k})$ reflects how much criterion $k$'s composite score differentiates provinces (after within-criterion redundancy has been removed), and (ii) \emph{inter-criterion uniqueness}: $\sum_{k'=1}^{K} (1 - r(\tilde{Z}_{\cdot k}, \tilde{Z}_{\cdot k'}))$ measures how much criterion $k$ provides information not already captured by other criteria. Critically, at this stage, correlation is computed across criteria (not sub-criteria), so a high $1 - r_{kk'}$ value means ``criterion $k$ varies independently of criterion $k'$,'' indicating minimal redundancy at the criterion level.

4. \textbf{Compute global criterion weights:}

\begin{equation}
\label{eq:weights_level2}
v_k = \frac{C_k}{\sum_{k'=1}^{K} C_{k'}} \quad \text{where} \quad \sum_{k=1}^{K} v_k = 1
\end{equation}

These weights, $\mathbf{v} = (v_1, \ldots, v_K)^\top$, represent the \emph{global importance coefficient} for each criterion, reflecting its discriminatory power and informational uniqueness at the criterion level. They directly answer: \textit{``After accounting for within-criterion redundancy (Level 1), which criteria are most informative about inter-provincial governance differentiation?''} Criteria with high $v_k$ are those whose composite scores (already optimized by Level 1 weighting) exhibit both large variance and low correlation with other criteria. Criteria with low $v_k$ either have low discriminatory power (most provinces achieve similar composite scores) or are highly redundant with peer criteria (composite score information is already captured elsewhere).

\textbf{Hierarchical Weight Synthesis via Product Rule.} The final set of 29 global sub-criterion weights is derived by combining Level 1 and Level 2 information via the product rule:

\begin{equation}
\label{eq:global_weights}
w_j = u_{k,j} \cdot v_k \quad \text{for all sub-criteria } j \in \text{SC}_k
\end{equation}

This product decomposes global importance into multiplicative components: each global weight $w_j$ is the product of (i)~its local rank within its parent criterion ($u_{k,j}$, the ``within-criterion importance'') and (ii)~the importance of that parent criterion globally ($v_k$, the ``global criterion importance''). \textbf{Hierarchical meaning:} This decomposition ensures non-compensatory hierarchical constraints:

\begin{itemize}[itemsep=3pt]
  \item \emph{No within-level compensation:} A sub-criterion with the highest $u_{k,j}$ in a low-$v_k$ criterion cannot achieve high global weight, because multiplying a large local weight by a small global criterion weight yields a small global sub-criterion weight. Conversely, even a modest local weight inherits the importance of a globally important criterion.
  
  \item \emph{Interpretability:} The product form is intuitive: a physician's sub-criterion (e.g., ``quality of maternal healthcare'') under Criterion 6 (Public Service Delivery) inherits importance both from (a) being the highest-variance healthcare indicator (high $u_{k,j}$) and (b) healthcare delivery being a critical determinant of provincial governance (high $v_k$). If either factor is weak, the global weight is modest; both must be strong for the global weight to be prominent.
  
  \item \emph{Information preservation:} All 29 sub-criteria retain positive weights (since $u_{k,j} > 0$ and $v_k > 0$ for all $k, j$), ensuring that every dimension of the governance index contributes to the final assessment, albeit with data-driven proportionality.
\end{itemize}

\textbf{Formal Constraint Satisfaction (Simplex Preservation Theorem):} The global weights automatically satisfy the fundamental probability simplex constraint:

\begin{equation}
\label{eq:simplex_proof}
\sum_{k=1}^{K} \sum_{j=1}^{n_k} w_j = \sum_{k=1}^{K} v_k \underbrace{\sum_{j=1}^{n_k} u_{k,j}}_{= 1} = \sum_{k=1}^{K} v_k = 1
\end{equation}

\textbf{Proof sketch:} For each criterion $k$, by definition Level 1 weights satisfy $\sum_{j=1}^{n_k} u_{k,j} = 1$ (they are normalized on criterion $k$'s simplex). Summing the global weights across all sub-criteria in criterion $k$ yields $\sum_{j=1}^{n_k} w_j = v_k \cdot 1 = v_k$. Summing across all criteria $k = 1, \ldots, K$ then yields $\sum_{k=1}^{K} v_k = 1$, since $v_k$ are Level 2 weights normalized to the global simplex. Thus, global weights sum exactly to unity without ad hoc re-normalization (though a floating-point numerical guard is typically applied for computational stability), confirming that the hierarchical product rule preserves the necessary probabilistic structure.

\textbf{Final Aggregation and Analysis Pipeline.} These 29 globally-normalized weightsare now passed to both the Hierarchical \MCDM ranking pipeline (Section~\ref{subsec:mcdm}) and to the ensemble forecasting pipeline (Sections~\ref{subsec:base_models} onwards). The two-level framework, represented by weights $\mathbf{w} = (w_1, \ldots, w_{29})^\top$, constitutes the objective, data-driven prioritization of information across all governance dimensions.

\subsubsection{Weighting Analysis}

\textbf{Temporal Stability Analysis: Window-Based Assessment}

The split-half test provides a binary temporal stability verdict. To capture more nuanced temporal dynamics and characterize weight evolution across the full 14-year window, we employ a window-based approach that extracts multiple overlapping time windows and computes agreement statistics across them. This approach is more statistically powerful than binary tests and provides actionable information about \textit{when} and \textit{where} weight shifts occur.

\textbf{Motivation:} A core assumption in governance assessment is that the prioritization of criteria—their relative importance for discriminating provinces—remains stable across time. Substantial drift in weights over 14 years would suggest either cumulative data quality degradation, genuine structural breaks in governance patterns requiring time-variant analysis, or both. A robust weighting system should exhibit temporal consistency, enabling the use of a single unified weight vector across all observation years.

\textbf{Methodological approach:} Rather than a single binary temporal stability test, we employ a window-based approach that extracts multiple overlapping time windows and computes rank agreement metrics across them. This approach is statistically more powerful than binary tests and provides disaggregated information identifying \textit{when} and \textit{where} weight instability emerges, should it occur.

\textbf{Window construction:} The 14-year panel (2011--2024) is decomposed into overlapping time windows of fixed length $L = 5$ years with unit step size (consecutive windows overlap by 4 years). This yields $(T - L) + 1 = 10$ distinct windows:

\begin{equation}
\text{Window}_k = [\text{year}_{\min} + (k-1), \ldots, \text{year}_{\min} + (k-1) + 4] \quad \text{for } k = 1, 2, \ldots, 10
\end{equation}

For each window, a mean weight vector is computed by averaging the criterion weights across the constituent years:

\begin{equation}
\bar{\mathbf{w}}_k = \frac{1}{L} \sum_{t \in \text{Window}_k} \mathbf{w}_t
\end{equation}

This produces 10 window-specific mean weight vectors, each representing the average prioritization scheme in a 5-year epoch. Comparisons among these vectors reveal medium-term weight trajectories and any persistent deviations.

\textbf{Spearman's rank correlation across windows:} The ordinal ranking of criteria may drift due to temporal shifts in governance dynamics. To quantify this drift sensitively, we compute Spearman's rank correlation coefficient $\rho$ between consecutive windows. For windows $k$ and $k+1$, define $\text{rank}_k(j)$ as the ordinal rank of criterion $j$ when all 29 criteria are sorted by mean weight $\bar{w}_{k,j}$ (ascending). Then:

\begin{equation}
\rho_k = 1 - \frac{6 \sum_{j=1}^{n} (\text{rank}_k(j) - \text{rank}_{k+1}(j))^2}{n(n^2 - 1)}
\end{equation}

This yields $W - 1 = 9$ pairwise rank correlations across consecutive windows. High mean correlation (e.g., $\bar{\rho} > 0.75$) signals stable criterion orderings; deviations from this threshold indicate reorderings worthy of investigation. The standard deviation $\sigma_{\rho}$ of correlations across windows captures volatility, identifying whether instability is episodic or persistent.

\textbf{Kendall's W: Omnibus agreement coefficient:} While pairwise Spearman correlations characterize adjacent-window agreement, we employ Kendall's coefficient of concordance $W$ to obtain a single omnibus statistic measuring agreement across \textit{all} 10 windows simultaneously. This statistic quantifies the global consistency of criterion rankings across the full temporal span:

\begin{equation}
W = \frac{12S}{m^2(n^3 - n)}
\end{equation}

where $m = 10$ (number of windows), $n = 29$ (number of criteria), and $S = \sum_{j=1}^{n} (R_j - \bar{R})^2$ is the sum of squared rank deviations, with $\bar{R} = \frac{m(n+1)}{2}$ as the theoretical mean rank. The coefficient ranges $W \in [0, 1]$: $W = 1$ indicates identical criterion rankings in all windows (perfect agreement), while $W = 0$ indicates independent, random rankings. For the \PAPI dataset, $W$ serves as a global temporal stability indicator.

\textbf{Coefficient of variation analysis:} While Spearman's $\rho$ and Kendall's $W$ measure ranking position stability, they are insensitive to changes in weight magnitudes. The Coefficient of Variation (CV) addresses this by capturing absolute weight variability. For each criterion $j$, compute:

\begin{equation}
\text{CV}_j = \frac{\sigma_j}{\bar{w}_j}
\end{equation}

where $\sigma_j$ and $\bar{w}_j$ are the standard deviation and mean of criterion $j$'s weight across all 14 individual years. CV values range $[0, \infty)$: CV $< 0.10$ indicates highly stable weight magnitude; CV $\in [0.10, 0.30]$ indicates moderate variation; CV $> 0.30$ signals substantial weight volatility. Computing CV for all 29 criteria yields a per-criterion sensitivity profile identifying which criteria exhibit most/least temporal stability. Criteria with low CV are reliable components of the weighting scheme, while high-CV criteria warrant additional scrutiny.

\textbf{Interpretation and reporting:} The window-based temporal stability analysis produces three complementary outputs: (i)~a time-series of 9 pairwise Spearman correlations, enabling identification of specific periods where ranking instability emerges; (ii)~a single Kendall's $W$ statistic summarizing global agreement across all windows; and (iii)~a per-criterion CV profile revealing which criteria are most temporally fragile. These metrics collectively establish whether the weight vector exhibits sufficient temporal consistency to justify its use as a unified parameter across all years 2011--2024, or whether time-variant weighting would be warranted.

\textbf{Sensitivity Analysis: Three-Tier Perturbation Framework}

\textbf{Motivation and complementarity:} While temporal stability assesses parameter consistency over time, sensitivity analysis addresses an orthogonal robustness question: \textit{How resilient are the final rankings to perturbations in weight values?} This resilience is essential because weight uncertainty arises from multiple sources: (i)~measurement error in the underlying governance sub-criteria, (ii)~model specification ambiguity in the hierarchical \CRITIC procedure, (iii)~legitimate alternative governance prioritizations reflecting different stakeholder preferences, and (iv)~sampling variability if the analysis were repeated with different cohorts or years. Sensitivity analysis quantifies how much ranking positions would change under plausible deviations from the point-estimate \CRITIC weights.

\textbf{Three-tier framework design:} We employ a Monte Carlo perturbation framework with three progressively intense perturbation magnitudes, progressively stressing the weight vector:

\begin{itemize}[itemsep=2pt]
  \item \textbf{Conservative tier (±5\%):} Reflects small measurement errors or minor model variations. If rankings prove stable under ±5\% weight perturbations, the weighting scheme is robust to small specification uncertainties.
  
  \item \textbf{Moderate tier (±15\%):} Reflects realistic policy revisions or substantial criterion data revisions (e.g., 2018 governance index redesign). Stability under ±15\% perturbations suggests resilience to non-trivial weight changes.
  
  \item \textbf{Aggressive tier (±50\%):} Represents extreme stress testing. Massive weight deviations (±50\%) simulate worst-case scenarios where governance assessment paradigms shift radically. Robustness here is unexpected but highly desirable.
\end{itemize}

\textbf{Perturbation procedure:} For each tier $t \in \{\text{conservative}, \text{moderate}, \text{aggressive}\}$, conduct $R = 1000$ independent Monte Carlo replicates. For replicate $r$:

\begin{enumerate}
  \item Generate random perturbations $\delta_{r,j} \sim \text{Uniform}(-m_t, +m_t)$ for each criterion $j$, with $m_t \in \{0.05, 0.15, 0.50\}$ corresponding to the three tiers.
  
  \item Apply perturbations to compute perturbed weights: $\tilde{w}_{r,j} = w^*_j (1 + \delta_{r,j})$.
  
  \item Apply non-negativity guard to ensure computational stability: $\tilde{w}_{r,j} := \max(\tilde{w}_{r,j}, 10^{-8})$.
  
  \item Re-normalize to enforce the probability simplex constraint $\sum_j \hat{w}_{r,j} = 1.0$:
  
  \begin{equation}
    \hat{w}_{r,j} = \frac{\tilde{w}_{r,j}}{\sum_{\ell=1}^{n} \tilde{w}_{r,\ell}}
  \end{equation}
  
  \item Re-rank all criteria by perturbed weights and compute the rank ordering change relative to the original.
\end{enumerate}

\textbf{Rank disruption metric:} For each replicate, quantify the magnitude of ranking disruption using Spearman's rank correlation between the original and perturbed criterion orderings:

\begin{equation}
\text{Disruption}_{r} = 1 - \rho(\text{rank}_{\text{original}}, \text{rank}_{\text{perturbed}, r})
\end{equation}

The disruption metric ranges $[0, 1]$: a value near 0 indicates that ranking remains stable despite perturbation (robust to weight variations), while values near 1 indicate substantial rank reordering (sensitive to weight specification). Aggregating across all 1000 replicates per tier yields the mean disruption $\bar{\text{Disruption}}_t$ for each tier $t$.

\textbf{Robustness scoring:} Define the robustness score for perturbation tier $t$ as:

\begin{equation}
\text{Robustness}_t = 1 - \bar{\text{Disruption}}_t \in [0, 1]
\end{equation}

By construction, robustness should decrease monotonically as perturbation intensity increases:

$$\text{Robustness}_{\text{conservative}} \geq \text{Robustness}_{\text{moderate}} \geq \text{Robustness}_{\text{aggressive}}$$

This monotonicity property is both expected and diagnostic: violation of the monotonicity order signals either numerical instability or weight configurations prone to tie-breaking sensitivity, warranting investigation. For a well-designed weighting system, conservative tier robustness should remain high (>0.85), indicating resilience to minor perturbations.

\textbf{Per-criterion sensitivity profiles:} Aggregation at the tier level masks criterion-specific patterns. To identify ``fragile'' criteria prone to rank reordering, compute for each criterion $j$ and tier $t$ the mean rank position change across all replicates:

\begin{equation}
\Delta\text{rank}_{t,j} = \frac{1}{R} \sum_{r=1}^{R} |\text{rank}_{\text{original}}(j) - \text{rank}_{\text{perturbed}}(r,j)|
\end{equation}

Values near 0 indicate ranking stability; larger values (up to $n-1 = 28$) indicate frequent rank shifts. Criteria with high $\Delta\text{rank}$ are \textit{sensitive} (their rank position fluctuates readily with weight changes), while those with low $\Delta\text{rank}$ are \textit{robust} (their ranking remains anchored). Computing this profile across all 29 criteria and 3 tiers produces a detailed sensitivity matrix revealing which criteria are most vulnerable to weight specification uncertainty. Such criteria merit careful review and may require additional validation before deployment in critical governance assessments.

\subsection{MCDM Ranking Methods}
\label{subsec:mcdm}

To construct a robust performance index that is invariant to methodological idiosyncrasies, we employ a multi-methodological framework comprising five distinct Multi-Criteria Decision Making (MCDM) algorithms. A known limitation of composite indexing is the sensitivity of the final ranking to the aggregation technique \citep{Greco2019}. By generating independent rankings utilizing distance-based, outranking, and proportional assessment paradigms, we establish a robust consensus evaluation that mitigates the risk of any single algorithm's mathematical artefacts dominating the governance ranking.

Let \( \tilde{X} \in \mathbb{R}^{m \times n} \) represent the performance matrix, where \( \tilde{x}_{ij} \in [0, 1] \) denotes the min-max normalized score of province \( i \) on sub-criterion \( j \) (as defined in Section~\ref{subsec:critic}), and \( w_j \) constitutes the corresponding global \CRITIC weight such that \( \sum_j w_j = 1 \). Given that the \PAPI assessment framework operates strictly with benefit-type indicators (as detailed in Table~\ref{tab:sc_properties}), cost-type formulations in the following algorithms are presented for generalized theoretical completeness but are effectively constrained to the benefit subspace in empirical application.

\subsubsection{TOPSIS}
\label{subsubsec:topsis}
The Technique for Order of Preference by Similarity to Ideal Solution (\TOPSIS) establishes rankings based on the geometric distance of an alternative from hypothetical ideal states \citep{Hwang1981}. The foundational premise of \TOPSIS is that the optimal alternative should simultaneously minimize the distance to the Positive Ideal Solution (PIS) and maximize the distance from the Negative Ideal Solution (NIS). This simultaneous geometric optimization is highly effective in differentiating alternatives that might otherwise appear similar under simple linear aggregation.

First, the normalized performance matrix is mapped into a weighted metric space: \( v_{ij} = w_j \tilde{x}_{ij} \). The PIS (\( A^+ \)) and NIS (\( A^- \)) vectors are determined by extracting the extremum performance values across all observed provinces:
\begin{align}
    A^+ &= \{ v_1^+, v_2^+, \dots, v_n^+ \} = \left\{ \max_i v_{ij} \right\} \\
    A^- &= \{ v_1^-, v_2^-, \dots, v_n^- \} = \left\{ \min_i v_{ij} \right\}
\end{align}

We measure the separation of each province \( i \) from these ideal solutions using the Euclidean distance metric (\( L_2 \) norm). The \( L_2 \) norm implies a compensatory relationship where severe underperformance in one criterion can be partially offset by strong outperformance in another, though the quadratic penalty disproportionately heavily weights extreme deviations:
\begin{equation}
    d_i^+ = \sqrt{ \sum_{j=1}^{n} (v_{ij} - v_j^+)^2 }, \quad d_i^- = \sqrt{ \sum_{j=1}^{n} (v_{ij} - v_j^-)^2 }
\end{equation}

The relative closeness coefficient, \( C_i \in [0, 1] \), synthesizes these two distances. It dictates the final ranking order, where a value closer to unity indicates superior alignment with the positive ideal:
\begin{equation}
    C_i = \frac{d_i^-}{d_i^+ + d_i^-}
\end{equation}

\subsubsection{VIKOR}
\label{subsubsec:vikor}
VlseKriterijumska Optimizacija I Kompromisno Resenje (\VIKOR) is rooted in compromise programming. It advances beyond simple distance minimization by establishing a ranking based on the particular measure of ``closeness'' to the ideal solution, explicitly balancing the maximum absolute ``group utility'' against the minimum individual regret of the ``opponent'' \citep{Opricovic2004}. Let \( f_j^* = \max_i \tilde{x}_{ij} \) and \( f_j^- = \min_i \tilde{x}_{ij} \) denote the theoretically best and worst values observed for criterion \( j \).

The algorithm calculates a multi-criteria utility measure, \( S_i \) (derived from the \( L_1 \) city-block distance norm, capturing aggregate consensus), and a regret measure, \( R_i \) (derived from the \( L_\infty \) Chebyshev distance norm, reflecting the maximum deviation across all criteria):
\begin{align}
    S_i &= \sum_{j=1}^{n} w_j \frac{f_j^* - \tilde{x}_{ij}}{f_j^* - f_j^-} \\
    R_i &= \max_j \left[ w_j \frac{f_j^* - \tilde{x}_{ij}}{f_j^* - f_j^-} \right]
\end{align}

The comprehensive compromise index, \( Q_i \), is subsequently aggregated as a convex combination of normalized utility and regret:
\begin{equation}
    Q_i = v \frac{S_i - S^*}{S^- - S^*} + (1 - v) \frac{R_i - R^*}{R^- - R^*}
\end{equation}
where \( S^* = \min_i S_i \), \( S^- = \max_i S_i \), \( R^* = \min_i R_i \), and \( R^- = \max_i R_i \). The strategic parameter \( v \in [0, 1] \) represents the weight given to the mechanism of maximum group utility (the majority rule), while \( (1-v) \) weights the individual regret (the veto of the most opposed criterion). In this study, we adopt the standard neutral consensus threshold \( v = 0.5 \), ensuring balanced consideration. A lower \( Q_i \) score signifies better performance and less regret.

\subsubsection{PROMETHEE II}
\label{subsubsec:promethee}
The Preference Ranking Organization Method for Enrichment Evaluation (\textsc{promethee~ii}) diverges fundamentally from distance-based methods by constructing a complete pre-ranking through the modeling of continuous outranking relations \citep{Brans1985}. By utilizing pairwise comparisons, the method explicitly models the decision-maker's bounded rational preference structures, accommodating indifference thresholds where minor differences in scores are deemed statistically or practically inconsequential.

We implement a V-shape preference function with strict parameterization. Let \( d_j = \tilde{x}_{aj} - \tilde{x}_{bj} \) be the difference in performance between province \( a \) and province \( b \) on criterion \( j \). We define a preference threshold \( p = 0.3 \), beyond which preference is absolute, and an indifference threshold \( q = 0.1 \), beneath which the alternatives are considered strictly equivalent. The continuous preference degree \( P_j(a,b) \) is mathematically operationalized as:
\begin{equation}
    P_j(a,b) = 
    \begin{cases} 
        0 & \text{if } d_j \leq q \\
        \frac{d_j - q}{p - q} & \text{if } q < d_j \leq p \\
        1 & \text{if } d_j > p 
    \end{cases}
\end{equation}

This bounded functional form prevents an overwhelmingly large difference in one criterion from fully compensating for deficiencies in another, distinguishing \textsc{promethee} as a partially non-compensatory approach. The aggregated multi-criteria preference index is \( \pi(a,b) = \sum_{j=1}^{n} w_j P_j(a,b) \). The final net outranking flow, \( \Phi_{\text{net}}(a) \), which establishes the absolute ranking order (higher flow is superior), is derived from the balance of positive flow (dominance over others) and negative flow (subjugation to others):
\begin{equation}
    \Phi_{\text{net}}(a) = \frac{1}{m - 1} \sum_{b \neq a} \Big( \pi(a,b) - \pi(b,a) \Big)
\end{equation}

\subsubsection{COPRAS}
\label{subsubsec:copras}
The Complex Proportional Assessment (\COPRAS) algorithm evaluates alternatives by analytically computing the ratio of their performance concerning benefit criteria to their performance regarding cost criteria. This method is distinct because it evaluates both vectors simultaneously to ascertain multidimensional proportional utility \citep{Zavadskas1994}. For a mutually exclusive partition of benefit attributes (\( \mathcal{B} \)) and cost attributes (\( \mathcal{C} \)), the weighted sums bounding the alternative's efficacy and risk are:
\begin{equation}
    S_i^+ = \sum_{j \in \mathcal{B}} w_j \tilde{x}_{ij}, \quad S_i^- = \sum_{j \in \mathcal{C}} w_j \tilde{x}_{ij}
\end{equation}

The relative significance index, \( Q_i \), accommodates the inverse scaling of cost variables by embedding them in the harmonic sum proportion:
\begin{equation}
    Q_i = S_i^+ + \frac{\sum_{k=1}^{m} S_k^-}{S_i^- \sum_{k=1}^{m} \frac{1}{S_k^-}}
\end{equation}
Because the \PAPI framework strictly comprises benefit-oriented sub-criteria (\( \mathcal{C} = \emptyset \)), the penalization term inherently collapses, reducing the analytical formulation to \( Q_i = S_i^+ \). This reduction conceptually collapses \COPRAS to an additive structure mirroring simple weighted aggregation, nonetheless, the normalized utility degree \( U_i = Q_i / \max_k Q_k \), expressed as a percentage of the highest-performing alternative, forms the proportional final score (higher is better).

\subsubsection{EDAS}
\label{subsubsec:edas}
The Evaluation Based on Distance from Average Solution (\EDAS) introduces a paradigm shift by appraising alternatives based on their deviations from the cross-sectional mean performance, rather than evaluating them relative to theoretical extremum ideals (as in \TOPSIS or \VIKOR) \citep{Keshavarz2015}. This average-centric approach offers robust differentiation particularly when performance scores are highly clustered, as it penalizes underperformance while rewarding outperformance symmetrically around the true sample state.

The aggregate average state for each criterion \( j \) across all provinces is \( AV_j = \frac{1}{m} \sum_{i=1}^{m} \tilde{x}_{ij} \). The Positive Distance from Average (\( \text{PDA} \)) and Negative Distance from Average (\( \text{NDA} \)) for benefit criteria are normalized scales of deviation:
\begin{equation}
    \text{PDA}_{ij} = \frac{\max(0, \tilde{x}_{ij} - AV_j)}{AV_j}, \quad 
    \text{NDA}_{ij} = \frac{\max(0, AV_j - \tilde{x}_{ij})}{AV_j}
\end{equation}

The weighted sums of these positive and negative distance deviations (\( SP_i \) and \( SN_i \)) provide the magnitude of overall excellence and deficiency:
\begin{equation}
    SP_i = \sum_{j=1}^{n} w_j \text{PDA}_{ij}, \quad SN_i = \sum_{j=1}^{n} w_j \text{NDA}_{ij}
\end{equation}

Finally, these measures are structurally normalized cross-sectionally to bound the final Appraisal Score (\( AS_i \)):
\begin{equation}
    AS_i = \frac{1}{2} \left[ \frac{SP_i}{\max_k SP_k} + \left( 1 - \frac{SN_i}{\max_k SN_k} \right) \right]
\end{equation}
where \( AS_i \in [0,1] \) acts as the definitive composite index of relative efficacy, effectively balancing outperformance rewards against underperformance penalties.

\subsubsection{Comparative Analysis of MCDM Methodologies}

The five selected methods embody fundamentally distinct philosophical paradigms for aggregating multidimensional performance. A comprehensive comparison elucidates their respective strengths and applicability domains:

\begin{table}[!ht]
\centering
\caption{Comparative classification of MCDM methods}
\label{tab:mcdm_comparison}
\small
\begin{tabular}{c c c c c}
\toprule
\textbf{Method} & \textbf{Paradigm} & \textbf{Norm} & \textbf{Compensatory} & \textbf{Ideal Construct} \\
\midrule
\TOPSIS & Distance-based & $L_2$ (Euclidean) & Fully & Extremum (min/max) \\
\VIKOR & Compromise & $L_1 + L_\infty$ & Moderate & Extremum (min/max) \\
\textsc{promethee~ii} & Outranking & Pairwise & Partial & Pairwise preference \\
\COPRAS & Proportional & Ratio & Fully & Proportional sum \\
\EDAS & Average-distance & $L_\infty$ & Moderate & Mean performance \\
\bottomrule
\end{tabular}
\end{table}

\textbf{Compensatory vs.\ Non-Compensatory Trade-offs:} A critical distinction among MCDM methods concerns whether poor performance in one criterion can be fully offset by exceptional performance in another. \TOPSIS and \COPRAS are fully compensatory: mathematically, a province with extremely high performance in half the criteria but zero performance in the remainder remains viable for high ranking. \textsc{promethee~ii}, by contrast, enforces bounded indifference thresholds, making it partially non-compensatory—poor performance in any single criterion cannot be entirely masked. \VIKOR and \EDAS occupy intermediate territory through their norm-mixing strategies (combining $L_1$ and $L_\infty$ distances), penalizing extreme deviations while permitting some cross-criterion compensation. For governance assessment, this spectrum reflects nuanced policy priorities: full compensation suits scenarios where diverse governance strengths genuinely substitute for one another; non-compensation better reflects situations where all dimensions are essential minima (e.g., corruption control).

\textbf{Sensitivity to Extreme Values and Outliers:} The choice of distance norm directly determines sensitivity to outlier provinces. The $L_2$ norm (Euclidean, used by \TOPSIS) is highly sensitive to large deviations—a province at extreme distance from the ideal disproportionately influences distances of all peers. The $L_1$ norm (Manhattan, used in \VIKOR's utility measure) and $L_\infty$ norm (Chebyshev, maximum deviation) are more robust: \VIKOR's regret measure ($R_i$) focuses only on the single-worst-performing criterion, inherently down-weighting balanced mediocrity. \EDAS's normalization by sample mean similarly constrains sensitivity to global scale distortions, making it particularly robust when provincial governance performance clusters tightly (as is common in single-country datasets where institutional frameworks are broadly similar).

\textbf{Ideological Reference Points:} All five methods must implicitly or explicitly define what constitutes an ''ideal'' province. \TOPSIS and \VIKOR employ empirical ideals: the best-observed performance in each criterion becomes the aspirational target. This reflects a revealed-preference philosophy: if no province has achieved a performance level, we do not demand it. Conversely, \EDAS anchors to the cross-sectional mean, treating the typical province as the reference point. This mean-centric approach is philosophically distinct—it rewards deviation from the norm rather than approximation to excellence, suitable for detecting emerging leaders or persistent laggards. \COPRAS's proportional framework is agnostic to absolute ideals, instead evaluating the ratio of aggregated strengths to aggregated weaknesses. \textsc{promethee~ii}'s pairwise framework transcends the need for a global ideal entirely, instead establishing a relational ranking solely based on pairwise preference magnitudes.

\subsubsection{Consensus and Ranking Stability}

A fundamental methodological strength of our multi-method ensemble is the emergent agreement structure among algorithmically distinct approaches. We quantify inter-method consensus using \textbf{Kendall's $W$ concordance coefficient} \citep{Kendall1948}:

\begin{equation}
\label{eq:kendall_w}
W = \frac{12 S}{m^2 (k^3 - k)}
\end{equation}

where $S = \sum_{i=1}^{m} \left( \sum_{j=1}^{k} r_{ij} - \frac{k(m+1)}{2} \right)^2$, $m$ is the number of provinces, $k$ is the number of methods (here, $k = 5$), and $r_{ij}$ is the rank of province $i$ under method $j$. $W \in [0, 1]$ measures concordance: $W \to 1$ indicates that all methods produce identical rankings; $W \to 0$ indicates statistical independence. For governance indexing, high $W$ (e.g., $W > 0.85$) provides confidence that the composite index reflects genuine provincial differences rather than methodological artifacts.

Our hypothesis is that $W > 0.80$ across all years, indicating that despite fundamental algorithmic differences, the five MCDM methods converge on a robust consensus ranking. This convergence simultaneously testifies to the stability of underlying provincial governance trajectories and guards against idiosyncratic algorithmic biases. Any province with dramatically different rankings across methods signals ambiguous governance status—potentially masking internal heterogeneity (e.g., some dimensions strong, others weak) worthy of policy investigation.

\subsection{Ensemble Machine Learning Forecasting}
\label{subsec:ensemble_forecasting}
The forecasting stage is formulated as a one-step-ahead multivariate prediction problem on the provincial panel. For province $i \in \{1, \ldots, N\}$ and year $t \in \{1, \ldots, T-1\}$, let
\begin{equation}
\mathbf{y}_{i,t} = \big(y_{i,t}^{(1)}, \ldots, y_{i,t}^{(K)}\big)^\top \in [0,1]^K
\end{equation}
denote the vector of $K = 8$ criterion scores after the chosen monotone target transformation and rescaling. The learning problem is to estimate a function $f$ such that
\begin{equation}
\widehat{\mathbf{y}}_{i,t+1} = f\!\left(\phi(\mathcal{H}_{i,t})\right), \qquad
\mathcal{H}_{i,t} = \{\mathbf{y}_{i,1}, \ldots, \mathbf{y}_{i,t}\},
\end{equation}
where $\phi(\cdot)$ is a feature map that converts each province's history into a supervised learning design matrix. Because the sample is small for modern forecasting standards, the architecture deliberately combines low-bias, low-variance, and distributional learners rather than relying on a single high-capacity model. This design is consistent with the project documentation and with the empirical bias-variance properties of stacked ensembles for small-to-medium panels \citep{vanDerLaan2007}.

The feature matrix is constructed from temporally ordered panel histories, while structurally undefined values generated by short histories are completed by the same MICE-based reducer used elsewhere in the project \citep{Doove2014,vanBuuren2018}. In practical terms, the engineering step preserves the information in early-year lagged and rolling features through imputation, while retaining binary missingness indicators so that downstream learners can distinguish observed from reconstructed history. The target is transformed by a monotone map before estimation, using a logit transform for bounded indices and a variance-stabilizing alternative for raw scores, so that Gaussian learners operate on approximately unbounded support while the inverse transform preserves rank order after prediction.

\subsubsection{Overview and System Architecture}
The forecasting system is organised as a three-layer ensemble. Layer 1 comprises five heterogeneous base learners that span tree-based, Bayesian linear, kernel-based, and distributional modeling families. Layer 2 is a Super Learner meta-ensemble that combines the out-of-fold predictions from Layer 1 into criterion-specific convex weights. Layer 3 calibrates prediction intervals using conformal methods so that point forecasts are accompanied by distribution-free uncertainty statements. This separation of roles is important: the base learners are optimized for predictive accuracy, the meta-learner is optimized for ensemble aggregation, and the conformal layer is optimized for interval validity.

Let $\mathbf{X}_{i,t} = \phi(\mathcal{H}_{i,t})$ denote the engineered feature vector. The pipeline first maps $\mathbf{X}_{i,t}$ into two estimator-specific preprocessing tracks. Tree-based learners operate on a threshold-only track that preserves the original scale and monotone ordering of the features, whereas Bayesian Ridge, Kernel Ridge Regression, and Support Vector Regression are trained on a supervised compression track built from Partial Least Squares to reduce collinearity and to focus the linear and kernel learners on covariance-relevant directions. The resulting base forecasts are then stacked through a constrained meta-learner. For the $m$-th base learner and the $k$-th criterion, let $\widehat{y}_{i,t+1,m}^{(k)}$ denote the corresponding point prediction. The final forecast is of the form
\begin{equation}
\widehat{y}_{i,t+1}^{(k)} = \sum_{m=1}^{M} \alpha_{m}^{(k)} \, \widehat{y}_{i,t+1,m}^{(k)},
\qquad \alpha_{m}^{(k)} \ge 0, \qquad \sum_{m=1}^{M} \alpha_{m}^{(k)} = 1,
\end{equation}
where $M = 5$ base models and the weights are learned from out-of-fold data rather than in-sample fits. This architecture is particularly suited to the present panel because it respects the temporal ordering of the data and avoids the leakage that would arise from random cross-validation.

\subsubsection{Temporal Feature Engineering}
The predictor set is built from 12 feature blocks that summarize level, trend, persistence, dispersion, and relative position within each province's own trajectory and the cross-sectional distribution. For each criterion $k$, the basic lagged and rolling blocks are defined componentwise. The $h$-period rolling mean is
\begin{equation}
\overline{y}_{i,t}^{(k,h)} = \frac{1}{h} \sum_{s=0}^{h-1} y_{i,t-s}^{(k)},
\end{equation}
the first difference or momentum is
\begin{equation}
\Delta y_{i,t}^{(k)} = y_{i,t}^{(k)} - y_{i,t-1}^{(k)},
\end{equation}
and the second difference or acceleration is
\begin{equation}
\Delta^2 y_{i,t}^{(k)} = y_{i,t}^{(k)} - 2 y_{i,t-1}^{(k)} + y_{i,t-2}^{(k)}.
\end{equation}
These local summaries are complemented by exponentially weighted moving averages,
\begin{equation}
\mathrm{EWMA}_{i,t}^{(k,\lambda)} = \lambda y_{i,t}^{(k)} + (1-\lambda)\mathrm{EWMA}_{i,t-1}^{(k,\lambda)}, \qquad \lambda \in (0,1),
\end{equation}
which emphasize recent trajectories while retaining memory of earlier states. A linear trend feature is obtained by least squares over the available history in the current window,
\begin{equation}
\beta_{i,t}^{(k)} = \arg\min_{a,b} \sum_{s \in \mathcal{T}_{i,t}} \left(y_{i,s}^{(k)} - a - b s\right)^2,
\end{equation}
with at least three valid observations required for stability. The panel-relative blocks then map each province-year observation to within-year ranks, z-scores, and percentile changes, while cross-criterion diversity is summarized by the within-row dispersion across the eight criteria,
\begin{equation}
\mathrm{Div}_{i,t}^{\mathrm{sd}} = \operatorname{sd}\!\left( y_{i,t}^{(1)}, \ldots, y_{i,t}^{(K)} \right),
\qquad
\mathrm{Div}_{i,t}^{\mathrm{range}} = \max_{k} y_{i,t}^{(k)} - \min_{k} y_{i,t}^{(k)}.
\end{equation}
Finally, geographic dummies encode the five Vietnam regional clusters so that persistent spatial heterogeneity is available to the learner as a covariate rather than being absorbed into residual noise.

The resulting feature vector has a rich but still structured composition, which is important for small samples. It contains the current criterion levels, lagged values up to three periods, rolling summaries over windows of 2, 3, and 5 years, trend and curvature terms, expanding means, rolling skewness, diversity measures, and panel-relative indicators. This design intentionally creates a forecasting basis that is sensitive to both local inertia and medium-term turning points. In the implementation, the engineered features that are undefined for early years are not dropped; instead, they are imputed through the multivariate imputation layer so that the effective training sample remains as large as possible \citep{Rubin1987,Doove2014,vanBuuren2018}.

\subsubsection{Base Forecasting Models}
The base learner set is selected to cover complementary inductive biases rather than to maximize raw model count. CatBoost provides the nonlinear tree-based component. With a shared tree structure and a MultiRMSE objective, it estimates all eight criteria jointly, exploiting cross-criterion dependence while remaining robust to monotone transforms and feature scaling issues \citep{Prokhorenkova2018}. In simplified form, the objective can be written as
\begin{equation}
\mathcal{L}_{\mathrm{CatBoost}} = \sum_{i=1}^{n} \sum_{k=1}^{K} \left(y_{i}^{(k)} - f_{k}(\mathbf{x}_{i})\right)^2,
\end{equation}
where the shared boosting structure learns a common partition of feature space and then assigns criterion-specific terminal values. This joint fitting is preferable to fitting eight separate tree models when the sample is limited, because the criterion outputs are correlated and should inform one another.

Bayesian Ridge supplies the probabilistic linear track. With Gaussian prior and Gaussian noise assumptions,
\begin{equation}
\mathbf{y} = \mathbf{X}\boldsymbol{\beta} + \boldsymbol{\varepsilon}, \qquad
\boldsymbol{\varepsilon} \sim \mathcal{N}(\mathbf{0}, \sigma^2 \mathbf{I}), \qquad
\boldsymbol{\beta} \sim \mathcal{N}(\mathbf{0}, \lambda^{-1}\mathbf{I}),
\end{equation}
the posterior mean and variance are available in closed form, which makes the learner both stable and interpretable \citep{Bishop2006}. This component is especially useful when the features are strongly collinear, because the posterior shrinkage acts as a regularizer rather than a source of instability. Kernel Ridge Regression and Support Vector Regression provide the smooth nonlinear counterweight to the tree learner. Kernel Ridge solves
\begin{equation}
\min_{\boldsymbol{\alpha}} \; \lVert \mathbf{y} - \mathbf{K}\boldsymbol{\alpha} \rVert_2^2 + \lambda \boldsymbol{\alpha}^\top \mathbf{K}\boldsymbol{\alpha},
\end{equation}
where $\mathbf{K}$ is the Gram matrix induced by an RBF kernel, while SVR solves the standard $\varepsilon$-insensitive regularized risk minimization problem
\begin{equation}
\min_{\mathbf{w},b,\boldsymbol{\xi},\boldsymbol{\xi}^*} \frac{1}{2}\lVert \mathbf{w} \rVert_2^2 + C \sum_{i=1}^{n} (\xi_i + \xi_i^*)
\end{equation}
subject to the usual tube constraints. These two learners are conceptually distinct from CatBoost: they model smooth functional variation rather than recursive partitioning and therefore provide diversification in the ensemble risk profile \citep{Scholkopf2002,Vapnik1995}.

The final base learner is Quantile Random Forest, which estimates the conditional distribution of the target rather than only its conditional mean. For a new feature vector $\mathbf{x}_*$, the conditional quantile at level $\tau$ is estimated as
\begin{equation}
\widehat{q}_{\tau}(\mathbf{x}_*) = \inf \left\{ y : \widehat{F}_{\mathbf{x}_*}(y) \ge \tau \right\},
\end{equation}
where $\widehat{F}_{\mathbf{x}_*}$ is the forest-implied conditional distribution assembled from leaf-wise training responses \citep{Meinshausen2006}. This learner contributes two distinct functions to the stack. First, its point forecasts provide another diverse estimate of the conditional mean. Second, its quantile outputs are used later in the uncertainty layer to construct heteroscedastic intervals. The combination of CatBoost, Bayesian Ridge, Kernel Ridge, SVR, and Quantile Random Forest therefore spans tree, Bayesian linear, kernel, margin-based, and distributional modeling families, which is precisely the diversity required for a disciplined stacked ensemble.

\subsubsection{Super Learner Meta-Ensemble}
The meta-ensemble is a Super Learner in the sense of \citet{vanDerLaan2007}: the base learners are not averaged arbitrarily but combined through weights learned from out-of-fold predictions. Let $\widehat{\mathbf{Z}} \in \mathbb{R}^{n \times M}$ denote the matrix of out-of-fold predictions, where column $m$ contains the predictions of the $m$-th base learner on the observations not used to train that learner in a given fold. The criterion-specific stacking problem is then
\begin{equation}
\widehat{\boldsymbol{\alpha}}^{(k)}
=
\arg\min_{\boldsymbol{\alpha} \in \mathbb{R}^{M}}
\; \left\lVert \mathbf{y}^{(k)} - \widehat{\mathbf{Z}}^{(k)} \boldsymbol{\alpha} \right\rVert_2^2
 + \lambda \lVert \boldsymbol{\alpha} \rVert_2^2,
\qquad
\text{s.t. } \boldsymbol{\alpha} \ge 0, \; \mathbf{1}^\top \boldsymbol{\alpha} = 1.
\end{equation}
The positivity and simplex constraints are substantive rather than cosmetic. They prevent cancellation between learners, preserve interpretability, and ensure that the final ensemble remains a convex combination of valid predictions. Because the forecasting task is multivariate, each criterion obtains its own weight vector $\widehat{\boldsymbol{\alpha}}^{(k)}$, so the combination can adapt to the fact that some base models are more effective for certain criteria than for others. For example, the tree learner tends to dominate when nonlinear threshold effects are present, whereas Bayesian Ridge and Kernel Ridge typically receive higher weights when the signal is smoother and more nearly linear.

The stacking stage uses walk-forward cross-validation over calendar years rather than random splits. If $\tau_1 < \tau_2 < \cdots < \tau_S$ denotes the ordered validation years, then fold $s$ trains on years up to $\tau_s - 1$ and validates on year $\tau_s$. This preserves the causal direction of time and prevents future information from contaminating model selection. The resulting out-of-fold matrix is therefore a genuine estimate of out-of-sample performance, not an in-sample approximation. After the weights are learned, all base learners are refit on the full training window and the final criterion forecast is obtained as the convex combination of their full-sample predictions.

\subsubsection{Conformal Prediction Intervals}
Point forecasts are insufficient for policy analysis unless uncertainty is quantified explicitly. The interval layer therefore calibrates the stacked point predictor using conformal prediction, which provides finite-sample coverage under exchangeability and remains practically useful when applied with empirical validation on temporal panels \citep{Vovk2005}. For symmetric calibration based on out-of-fold residuals, let $e_i = y_i - \widehat{y}_i^{\mathrm{oof}}$ denote the held-out residuals and let
\begin{equation}
\widehat{q}_{1-\alpha} = \operatorname{Quantile}_{\lceil (n+1)(1-\alpha) \rceil / n} \left( |e_1|, \ldots, |e_n| \right).
\end{equation}
The resulting interval for a new observation is
\begin{equation}
\mathcal{I}_{1-\alpha}(\mathbf{x}_*) = \left[ \widehat{y}(\mathbf{x}_*) - \widehat{q}_{1-\alpha},\; \widehat{y}(\mathbf{x}_*) + \widehat{q}_{1-\alpha} \right].
\end{equation}
When the predictive distribution is clearly asymmetric or heteroscedastic, the pipeline can instead calibrate the quantile outputs of the Quantile Random Forest through conformalized quantile regression. In that case, with lower and upper forest quantiles $\widehat{q}_{\alpha/2}(\mathbf{x})$ and $\widehat{q}_{1-\alpha/2}(\mathbf{x})$, the conformity score is
\begin{equation}
s_i = \max\!\left\{ \widehat{q}_{\alpha/2}(\mathbf{x}_i) - y_i,\; y_i - \widehat{q}_{1-\alpha/2}(\mathbf{x}_i) \right\},
\end{equation}
and the calibrated interval becomes
\begin{equation}
\mathcal{I}_{1-\alpha}^{\mathrm{CQR}}(\mathbf{x}_*) = \left[ \widehat{q}_{\alpha/2}(\mathbf{x}_*) - \widehat{s}_{1-\alpha},\; \widehat{q}_{1-\alpha/2}(\mathbf{x}_*) + \widehat{s}_{1-\alpha} \right],
\end{equation}
with $\widehat{s}_{1-\alpha}$ obtained from the empirical distribution of $\{s_i\}$ \citep{Romano2019}. This construction is well suited to governance data because the forecast uncertainty is not constant across provinces or criteria.

To track nonstationary calibration drift, the implementation also supports adaptive conformal updating. If $\mathbb{1}\{y_t \notin \mathcal{I}_t\}$ is the miscoverage indicator at time $t$, then the nominal miscoverage level is updated by
\begin{equation}
\alpha_{t+1} = \alpha_t + \gamma \left( \alpha - \mathbb{1}\{ y_t \notin \mathcal{I}_t \} \right),
\end{equation}
with a small step size $\gamma$ so that the interval width adjusts gradually to structural shifts rather than overreacting to single misses \citep{Gibbs2021}. In this paper, conformal intervals are therefore interpreted as calibrated empirical uncertainty bands on the panel scale, with their coverage assessed out of sample rather than assumed mechanically from idealized exchangeability.

\subsubsection{Evaluation Metrics and Validation}
Forecast accuracy is reported using a standard collection of point and interval metrics. For a given criterion $k$ with $n$ test observations and residuals $e_i^{(k)} = y_i^{(k)} - \widehat{y}_i^{(k)}$, the coefficient of determination is
\begin{equation}
R_k^2 = 1 - \frac{\sum_{i=1}^{n} \left(e_i^{(k)}\right)^2}{\sum_{i=1}^{n} \left(y_i^{(k)} - \overline{y}^{(k)}\right)^2},
\qquad
\overline{y}^{(k)} = \frac{1}{n} \sum_{i=1}^{n} y_i^{(k)}.
\end{equation}
The remaining error measures are
\begin{align}
\mathrm{RMSE}_k &= \left( \frac{1}{n} \sum_{i=1}^{n} \left(e_i^{(k)}\right)^2 \right)^{1/2},
&
\mathrm{MAE}_k &= \frac{1}{n} \sum_{i=1}^{n} \left| e_i^{(k)} \right|, \\
\mathrm{MedAE}_k &= \operatorname{median}\!\left( \left| e_1^{(k)} \right|, \ldots, \left| e_n^{(k)} \right| \right),
&
\mathrm{MAPE}_k &= \frac{100}{n} \sum_{i=1}^{n} \left| \frac{e_i^{(k)}}{\max\!\left( |y_i^{(k)}|, \varepsilon \right)} \right|, \\
\mathrm{MaxErr}_k &= \max_{1 \le i \le n} \left| e_i^{(k)} \right|,
&
\mathrm{Bias}_k &= \frac{1}{n} \sum_{i=1}^{n} e_i^{(k)},
\end{align}
where $\varepsilon$ is a small numerical guard used only to prevent division by zero. These metrics are computed per criterion and then averaged across criteria and walk-forward folds to obtain a stable summary of model performance. The interval layer is evaluated with empirical coverage, average width, and the Winkler score, while residual behavior is checked with the Durbin-Watson statistic,
\begin{equation}
DW = \frac{\sum_{i=2}^{n} \left(e_i - e_{i-1}\right)^2}{\sum_{i=1}^{n} e_i^2},
\end{equation}
the Breusch-Pagan test for heteroscedasticity, and the Shapiro-Wilk test for residual normality. Validation follows the same walk-forward chronology used to train the meta-learner, so the reported numbers are genuinely out-of-sample summaries rather than resubstitution fits. This is the appropriate protocol for a 14-year panel in which temporal dependence, structural breaks, and heterogeneous missingness all matter to forecast quality.

% =============================================================
\section{Results}
\label{sec:results}
% =============================================================

\subsection{CRITIC Weighting}
\label{subsec:results_weights}

\textit{[Content placeholder.]}

\subsection{Historical Provincial Rankings (2011--2024)}
\label{subsec:results_historical}
% ----------------------------------------------------------------
% PLACEHOLDER — Present Hierarchical MCDM results for all years.
% Kendall's W ~ 0.88 (strong inter-method agreement).
% Per-criterion MCDM score comparisons (TOPSIS, VIKOR, PROMETHEE II,
%   COPRAS, EDAS, SAW).
% Figure: parallel coordinate plot of per-criterion scores.
% Table 3: Top 10 provinces by SAW composite score, latest year (2024).
% Trend analysis: provinces improving/declining over 14 years.
% ----------------------------------------------------------------
\textit{[Content placeholder.]}

\subsection{Inter-Method Concordance and Robustness}
\label{subsec:results_concordance}
% ----------------------------------------------------------------
% PLACEHOLDER — Kendall's W concordance across 6 MCDM methods.
% Sensitivity analysis: 100+ Monte Carlo simulations with ±15%
%   weight perturbations. Robustness index and confidence intervals.
% Spearman rank correlations across methods.
% ----------------------------------------------------------------
\textit{[Content placeholder.]}

\subsection{Forecasting Model Performance}
\label{subsec:results_forecast_performance}
% ----------------------------------------------------------------
% PLACEHOLDER — 5-fold walk-forward CV R² per model:
%   BayesianRidge: 0.1304 ± 0.0514 (best individual)
%   KernelRidge:   0.1213 ± 0.0365 (most stable)
%   CatBoost:      0.1008 ± 0.0621
%   SVR:           0.0757 ± 0.0313
%   QuantileRF:   -0.0873 ± 0.1104
% Super Learner meta-weights:
%   BayesianRidge 49.0%, KernelRidge 19.1%, CatBoost 11.7%,
%   SVR 8.6%, QuantileRF 8.6%
% Holdout (2024 withheld, 252 OOF samples):
%   R² = 0.2171, RMSE = 2.3936, MAE = 1.1700
% Residual diagnostics: Durbin-Watson, Breusch-Pagan, Shapiro-Wilk.
% Figure: CV boxplots, feature importance heatmap, model weight chart.
% ----------------------------------------------------------------
\textit{[Content placeholder.]}

\subsection{2025 Provincial Governance Forecasts and Prediction Intervals}
\label{subsec:results_forecast_2025}
% ----------------------------------------------------------------
% PLACEHOLDER — 63-province 2025 forecasts for 8 criteria (SAW-normalised [0,1]).
% 95% conformal prediction intervals for each province-criterion cell.
% Interval width analysis: tightest vs. widest intervals by criterion.
% Table 4: Top 10 provinces in 2025 forecast ranking.
% Figure: prediction interval chart for selected provinces.
% Figure: conformal coverage calibration curve.
% ----------------------------------------------------------------
\textit{[Content placeholder.]}

\subsection{Integrated MCDM Ranking of 2025 Forecasts}
\label{subsec:results_2025_ranking}
% ----------------------------------------------------------------
% PLACEHOLDER — Apply CRITIC weights and 6 MCDM methods to 2025 forecasts.
% Produce 2025 forecast-based provincial ranking.
% Compare with 2024 historical ranking: rank shifts.
% Table 5: Full 63-province 2025 MCDM ranking and rank-change vs. 2024.
% ----------------------------------------------------------------
\textit{[Content placeholder.]}

% =============================================================
\section{Discussion}
\label{sec:discussion}
% =============================================================

\subsection{Interpretation of CRITIC Weights}
\label{subsec:disc_weights}
% ----------------------------------------------------------------
% PLACEHOLDER — Explain why C05 (Public Admin Procedures, 19.6%) receives
% the highest weight: high inter-provincial variance and low correlation
% with other criteria. Contrast with C07/C08 (low weights due to structural
% gap in early years reducing effective variance). Policy implications:
% administrative reform has highest leverage for differentiation.
% ----------------------------------------------------------------
\textit{[Content placeholder.]}

\subsection{MCDM Method Convergence and Governance Interpretation}
\label{subsec:disc_mcdm}
% ----------------------------------------------------------------
% PLACEHOLDER — W ≈ 0.88 confirms rankings are stable across methodological
% choices. Discuss cases where methods diverge (e.g., VIKOR vs TOPSIS in
% mid-ranking provinces) and how ER handles residual disagreement.
% Interpret top/bottom provinces. Connection to Vietnam Gov't policy targets.
% ----------------------------------------------------------------
\textit{[Content placeholder.]}

\subsection{Forecasting Performance in Small-Panel Contexts}
\label{subsec:disc_forecast}
% ----------------------------------------------------------------
% PLACEHOLDER — Individual model R² (0.07–0.13) is modest but expected for
% highly persistent panel data with structural breaks (COVID-19, sub-criteria
% introduction). The Super Learner's NNLS combination allocates near-zero
% weight to QRF when uncertainty is high (tree methods can overfit small T), while
% Bayesian Ridge (49%) and KernelRidge (19%) reflect suitability of
% regularised linear methods for small-T panels. Compare with benchmark
% (random walk, AR(1)). Holdout R² = 0.22 represents genuine out-of-sample
% predictive power.
% ----------------------------------------------------------------
\textit{[Content placeholder.]}

\subsection{Conformal Prediction Interval Quality}
\label{subsec:disc_conformal}
% ----------------------------------------------------------------
% PLACEHOLDER — Interval width variation across criteria: wider for criteria
% with structural breaks (C07, C08 missing early years), narrower for stable
% criteria (C01, C02). Empirical coverage vs. nominal 95%. Comparison with
% naive ±1.96*residual_std approach. Winkler score analysis.
% ----------------------------------------------------------------
\textit{[Content placeholder.]}

\subsection{Policy Implications for Vietnam's Governance Reform}
\label{subsec:disc_policy}
% ----------------------------------------------------------------
% PLACEHOLDER — Three actionable insights:
% (1) Provinces consistently underperforming on SC32 (govt responsiveness)
%     should be prioritised for judicial and public complaint reform.
% (2) The large 2025 forecast uncertainty bands for C07/C08 reflect
%     volatile growth in environmental enforcement and digital government;
%     policy investment in these areas should be accompanied by mid-year
%     monitoring.
% (3) The CRITIC-identified importance of C05/C06 suggests that national-level
%     administrative simplification programmes (e.g., single-window systems)
%     yield the highest marginal improvement in composite scores.
% ----------------------------------------------------------------
\textit{[Content placeholder.]}

\subsection{Comparison with Related Approaches}
\label{subsec:disc_comparison}
% ----------------------------------------------------------------
% PLACEHOLDER — Contrast with:
% (a) World Bank WGI (country-level, no sub-national differentiation)
% (b) PCI (Vietnam business climate index — focuses on investment climate,
%     not citizen governance)
% (c) Standard MCDM papers using entropy or AHP for weighting
% (d) ARIMA/VAR-based forecasting of governance indicators
% Advantages: objective weighting, multi-method consensus, ML forecasting,
%             distribution-free intervals, reproducible open-source pipeline.
% ----------------------------------------------------------------
\textit{[Content placeholder.]}

\subsection{Limitations}
\label{subsec:disc_limitations}
% ----------------------------------------------------------------
% PLACEHOLDER —
% (1) Survey-based data susceptible to political economy biases and mode effects.
% (2) Small T (14 years) limits statistical power of walk-forward CV and
%     motivates parsimonious models; forecasting gains are modest.
% (3) MCDM methods assume all-benefit (monotone) criteria and a static
%     preference structure; non-compensatory preferences not captured.
% (4) Conformal calibration pool (n_cal < 50 for some criteria-strata) may
%     yield conservative intervals under Mondrian stratification.
% (5) Causal interpretation of regression coefficients is not warranted;
%     the framework is predictive, not structural.
% ----------------------------------------------------------------
\textit{[Content placeholder.]}

% =============================================================
\section{Conclusion}
\label{sec:conclusion}
% =============================================================
% ----------------------------------------------------------------
% PLACEHOLDER — Summary of contributions:
% (1) First application of two-level CRITIC weighting to PAPI data;
%     confirmed temporal stability (cosine 0.9915).
% (2) Six-method MCDM consensus via ER; Kendall's W ≈ 0.88.
% (3) Three-tier ensemble (6 base models + Super Learner + conformal) for
%     governance forecasting; holdout R² = 0.22; 95% conformal intervals.
% (4) First forward-looking PAPI ranking for 2025.
%
% Limitations recap and future work:
% - Extend to district/commune level as granular data become available.
% - Incorporate text-based sentiment from citizen complaint records.
% - Apply Phase II enhancements: CQR, Mondrian CP, group LASSO meta-weights.
% - Investigate causal mechanisms (e.g., fiscal transfers → C03/C04 improvement).
% ----------------------------------------------------------------
\textit{[Content placeholder.]}

% =============================================================
%  REFERENCES
% =============================================================

\bibliography{main}

\end{document}
